---
title: "Airings Channel Models"
output: html_document
---
 

```{r echo=FALSE, message=FALSE, warning=FALSE} 
library(tidyr)
library(dplyr)
library(openxlsx)
library(lubridate)
library(ggplot2)
library(gridExtra)
library(forecast)
library(stats)
library(pander)
library(TTR)
library(googlesheets)

source("report_functions.R")

```



```{r echo=FALSE, message=FALSE}
load(file="channel_sessions_long_airings.rda")
freq=365

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
channel_session_gathered=channel_sessions_long %>% gather(key=channel,value=sessions,2:6)
channel_session_gathered$Units="Sessions"
channel_session_gathered$Units[which(channel_session_gathered$channel=="Airings")]="Airings"

ggplot(channel_session_gathered)+theme_bw()+
  geom_line(aes(x=date,y=sessions,color=channel))+
  facet_grid(Units~.,scales="free")+ylab("")+xlab("Date")+
  ggtitle("Daily Airings And Channel Sessions")


```

```{r echo=FALSE, message=FALSE, warning=FALSE}
vars<-c("organic.net.home","organic.home","direct.net.home","direct.home","paid.brand.sessions")
#always sort by descending date first!!
ccf.df=data.frame(Correlation=NULL,Lag=NULL,Source=NULL)

for (var in vars) {
  ind=which(names(channel_sessions_long) == var)
  study_var=channel_sessions_long[,ind]
  na_inds=which(is.na(study_var))
  Airings=channel_sessions_long$Airings[-na_inds]
  study_var=na.omit(study_var)
  
  
  ccf_temp<-ccf(Airings,study_var,plot=FALSE)
  ccf_temp_df=data.frame(Correlation=ccf_temp$acf,Lag=ccf_temp$lag,Source=rep(var,length(ccf_temp$lag)))
  
  ccf.df<-rbind(ccf.df,ccf_temp_df)
}

ggplot(ccf.df %>% filter(Lag>=0),aes(x=Lag,y=Correlation,color=Source))+ theme_bw()+
  geom_point()+ggtitle("TV Airings Delayed Effect")+xlab("Lag (Days)")+
  scale_color_manual( values=rainbow(length(vars)),
                      name="Source",
                      breaks=vars,
                      labels=vars)


```

## Organic Net Home Channel

```{r echo=FALSE, message=FALSE}
study_var=channel_sessions_long$organic.net.home
na_inds=which(is.na(study_var))
Airings=channel_sessions_long$Airings[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]
title_paste="Organic Net Home"

```

###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be 52 (weeks per year), but we don't have two full periods
poly_fit=report_poly_fit_2(study_var,Airings)
report_poly_fit_2_sub(poly_fit,study_var)
```

###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
stepwise_model=step_model(study_var,Airings)
```

```{r echo=FALSE, message=FALSE}
step_pander(stepwise_model)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

poly_plots(Airings,study_var,poly_fit,stepwise_model)

```

###Trend Decomposition

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
stl_func(study_var,freq)

```



###ARIMAX model with Airings spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
Airings_arima=arima_func(stepwise_model,study_var,Airings,freq)
arima_func_sub(Airings_arima,stepwise_model,study_var,Airings,freq)

```


```{r echo=FALSE, message=FALSE}

# model_comp_plots(stepwise_model,Airings_arima)
transformed_plot(Airings_arima,Airings)
```

###Model Validation
```{r echo=FALSE, message=FALSE, warning=FALSE}
model_validation(Airings_arima,study_var,Airings,freq,date)
```

## Organic Home Channel

```{r echo=FALSE, message=FALSE}
study_var=channel_sessions_long$organic.home
na_inds=which(is.na(study_var))
Airings=channel_sessions_long$Airings[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="Organic Home"
```
###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be 52 (weeks per year), but we don't have two full periods
poly_fit=report_poly_fit_2(study_var,Airings)
report_poly_fit_2_sub(poly_fit,study_var)
```

###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
stepwise_model=step_model(study_var,Airings)
```

```{r echo=FALSE, message=FALSE}
step_pander(stepwise_model)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

poly_plots(Airings,study_var,poly_fit,stepwise_model)

```

###Trend Decomposition

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
stl_func(study_var,freq)

```



###ARIMAX model with Airings spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
Airings_arima=arima_func(stepwise_model,study_var,Airings,freq)
arima_func_sub(Airings_arima,stepwise_model,study_var,Airings,freq)

```


```{r echo=FALSE, message=FALSE}

# model_comp_plots(stepwise_model,Airings_arima)
transformed_plot(Airings_arima,Airings)
```

###Model Validation
```{r echo=FALSE, message=FALSE, warning=FALSE}
model_validation(Airings_arima,study_var,Airings,freq,date)

```

## Direct Net Home Channel

```{r echo=FALSE, message=FALSE}
study_var=channel_sessions_long$direct.net.home
na_inds=which(is.na(study_var))
Airings=channel_sessions_long$Airings[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="Direct Net Home"
```

###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be 52 (weeks per year), but we don't have two full periods
poly_fit=report_poly_fit_2(study_var,Airings)
report_poly_fit_2_sub(poly_fit,study_var)
```

###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
stepwise_model=step_model(study_var,Airings)
```

```{r echo=FALSE, message=FALSE}
step_pander(stepwise_model)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

poly_plots(Airings,study_var,poly_fit,stepwise_model)

```

###Trend Decomposition

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
stl_func(study_var,freq)

```



###ARIMAX model with Airings spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
Airings_arima=arima_func(stepwise_model,study_var,Airings,freq)
arima_func_sub(Airings_arima,stepwise_model,study_var,Airings,freq)

```


```{r echo=FALSE, message=FALSE}

# model_comp_plots(stepwise_model,Airings_arima)
transformed_plot(Airings_arima,Airings)
```

###Model Validation

```{r echo=FALSE, message=FALSE, warning=FALSE}
model_validation(Airings_arima,study_var,Airings,freq,date)
```

## Direcy Home Channel

```{r echo=FALSE, message=FALSE}
study_var=channel_sessions_long$direct.home
na_inds=which(is.na(study_var))
Airings=channel_sessions_long$Airings[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="Direct Home"
```
###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be 52 (weeks per year), but we don't have two full periods
poly_fit=report_poly_fit_2(study_var,Airings)
report_poly_fit_2_sub(poly_fit,study_var)
```

###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
stepwise_model=step_model(study_var,Airings)
```

```{r echo=FALSE, message=FALSE}
step_pander(stepwise_model)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

poly_plots(Airings,study_var,poly_fit,stepwise_model)

```

###Trend Decomposition

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
stl_func(study_var,freq)

```



###ARIMAX model with Airings spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
Airings_arima=arima_func(stepwise_model,study_var,Airings,freq)
arima_func_sub(Airings_arima,stepwise_model,study_var,Airings,freq)

```


```{r echo=FALSE, message=FALSE}

# model_comp_plots(stepwise_model,Airings_arima)
transformed_plot(Airings_arima,Airings)
```

###Model Validation

```{r echo=FALSE, message=FALSE, warning=FALSE}
model_validation(Airings_arima,study_var,Airings,freq,date)
```

## Paid Brand Channel

```{r echo=FALSE, message=FALSE}
study_var=channel_sessions_long$paid.brand.sessions
na_inds=which(is.na(study_var))
Airings=channel_sessions_long$Airings[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="Paid Brand"
```
###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be 52 (weeks per year), but we don't have two full periods
poly_fit=report_poly_fit_2(study_var,Airings)
report_poly_fit_2_sub(poly_fit,study_var)
```

###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
stepwise_model=step_model(study_var,Airings)
```

```{r echo=FALSE, message=FALSE}
step_pander(stepwise_model)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

poly_plots(Airings,study_var,poly_fit,stepwise_model)

```

###Trend Decomposition

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
stl_func(study_var,freq)

```



###ARIMAX model with Airings spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
Airings_arima=arima_func(stepwise_model,study_var,Airings,freq)
arima_func_sub(Airings_arima,stepwise_model,study_var,Airings,freq)

```


```{r echo=FALSE, message=FALSE}

# model_comp_plots(stepwise_model,Airings_arima)
transformed_plot(Airings_arima,Airings)
```

###Model Validation

```{r echo=FALSE, message=FALSE, warning=FALSE}
model_validation(Airings_arima,study_var,Airings,freq,date)
```
