---
title: "Airings Channel Models"
output: html_document
---
 

```{r echo=FALSE, message=FALSE, warning=FALSE} 
library(tidyr)
library(dplyr)
library(openxlsx)
library(lubridate)
library(ggplot2)
library(gridExtra)
library(forecast)
library(stats)
library(pander)

source("arima_formula.R")

```



```{r echo=FALSE, message=FALSE}
load(file="channel_sessions_long_airings.rda")

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
channel_session_gathered=channel_sessions_long %>% gather(key=channel,value=sessions,2:6)
channel_session_gathered$Units="Sessions"
channel_session_gathered$Units[which(channel_session_gathered$channel=="Airings")]="Airings"

ggplot(channel_session_gathered)+theme_bw()+
  geom_line(aes(x=date,y=sessions,color=channel))+
  facet_grid(Units~.,scales="free")+ylab("")+xlab("Date")+
  ggtitle("Daily Airings And Channel Sessions")


```

```{r echo=FALSE, message=FALSE, warning=FALSE}
vars<-c("organic.net.home","organic.home","direct.net.home","direct.home","paid.brand.sessions")

ccf.df=data.frame(Correlation=NULL,Lag=NULL,Source=NULL)

for (var in vars) {
  ind=which(names(channel_sessions_long) == var)
  study_var=channel_sessions_long[,ind]
  na_inds=which(is.na(study_var))
  Airings=channel_sessions_long$Airings[-na_inds]
  study_var=na.omit(study_var)
  
  
  ccf_temp<-ccf(Airings,study_var,plot=FALSE)
  ccf_temp_df=data.frame(Correlation=ccf_temp$acf,Lag=ccf_temp$lag,Source=rep(var,length(ccf_temp$lag)))
  
  ccf.df<-rbind(ccf.df,ccf_temp_df)
}

ggplot(ccf.df %>% filter(Lag>=0),aes(x=Lag,y=Correlation,color=Source))+ theme_bw()+
  geom_point()+ggtitle("TV Airings Delayed Effect")+xlab("Lag (Days)")+
  scale_color_manual( values=rainbow(length(vars)),
                      name="Source",
                      breaks=vars,
                      labels=vars)



```

## Organic Net Home Channel

```{r echo=FALSE, message=FALSE}
study_var=channel_sessions_long$organic.net.home
na_inds=which(is.na(study_var))
Airings=channel_sessions_long$Airings[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]
title_paste="Organic Net Home"

```

###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be 52 (weeks per year), but we don't have two full periods
poly_fit=lm(study_var~Airings+I(Airings^2))
tmp_df=data.frame(round(coef(poly_fit),3))
tmp_df=rbind(tmp_df,cor(fitted(poly_fit),na.omit(study_var))^2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
pander(tmp_df)

```


###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
big_poly_fit=lm(study_var~Airings+I(Airings^2)+I(Airings^3)+I(Airings^4))
stepwise_model=step(big_poly_fit,k=log(nrow(channel_sessions_long)),scope = list(lower = ~Airings))
```

```{r echo=FALSE, message=FALSE}
tmp_df=data.frame(round(coef(stepwise_model),3))
tmp_df=rbind(tmp_df,cor(fitted(stepwise_model),na.omit(study_var))^2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
pander(tmp_df)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
tmp_df=data.frame(Airings=Airings,channel=study_var,poly=fitted(poly_fit),
                  step=fitted(stepwise_model))
ggplot(tmp_df) + theme_bw()+
  # geom_smooth(aes(x=Airings,y=channel),method="smooth")+
  geom_point(aes(x=Airings,y=channel,color=title_paste))+ 
  geom_line(aes(x=Airings,y=poly,color="2nd Order Plynomial Fit"))+ 
  geom_line(aes(x=Airings,y=step,color="Stepwise Polynomial Fit"))+ 
  ggtitle("Model Fits")+xlab("Airings Speding (Dollars)")+ylab("Sessions")+
  guides(color=guide_legend(title="Models"))

#This plot shows a major time trend component- implying previous models were useless
t=Box.test(stepwise_model$residuals)
box_p=round(t$p.value,4)
qplot(channel_sessions_long$date[-na_inds],stepwise_model$residuals)+theme_bw()+
  ggtitle(paste("Polynomial Fit Residuals, Box Test p-value",box_p) )+xlab("Date")+ylab("Residuals")



```

###Trend Decomposition

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
ts_var=ts(study_var, frequency = 365)
stl_obj=stl(ts_var, s.window="periodic",robust=TRUE)
plot(stl_obj)+title(paste(title_paste,"Seasonal Trend Decomposition"))


qplot(date,Airings)+theme_bw()+ggtitle("Airings")+xlab("Date")+ylab("Dollars")

stl_residuals=stl_obj$time.series[,3]

temp_df=data.frame(Airings,stl_residuals)
ggplot(temp_df,aes(x=Airings,y=stl_residuals))+theme_bw()+
  geom_smooth(method="lm")+geom_point()+ggtitle("Airings Against Smoothed Residuals")+xlab("Dollars")+ylab("Residuals")
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
 new_r2=round(cor(Airings,stl_residuals),2)
 old_r2=round(cor(Airings,study_var),2)
 temp_df=data.frame(Message=c("Orignal Correlation:","Residuals Correlation:"),R2=c(old_r2,new_r2))
 pander(temp_df)

```


###ARIMAX model with Airings spend
```{r echo=FALSE, message=FALSE, warning=FALSE}

#Not allowing for seasonal component until we have two years of data
Airings_arima=auto.arima(study_var,xreg=c(Airings),max.P=0,max.D = 0,max.Q = 0,allowdrift=FALSE,allowmean = FALSE)
 # Airings_arima=auto.arima(study_var,xreg=c(Airings),allowdrift=FALSE,allowmean = FALSE)

arima_formula(Airings_arima,Airings)


# Airings_arima_fcast=forecast(Airings_arima,xreg=c(Airings),h=0)
# plot(Airings_arima_fcast)



#Building coefficient and R2 table
Airings_arima_R2=round(cor(fitted(Airings_arima),ts_var)^2,2)
tmp_df=data.frame(coef(Airings_arima))
tmp_df=rbind(tmp_df,Airings_arima_R2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
pander(tmp_df)

```


```{r echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
#Secret manual modeling
##Attempting to build the arim simple enough for excel
#for (1,1,2) model
ma1=coef(Airings_arima)[grep("ma1",names(coef(Airings_arima)))]
ma2=coef(Airings_arima)[grep("ma2",names(coef(Airings_arima)))]
ar1=coef(Airings_arima)[grep("ar1",names(coef(Airings_arima)))]
Airings_coef=coef(Airings_arima)[grep("Airings",names(coef(Airings_arima)))]
 

e_terms=2
 man_pred=rep(NA,length(study_var))
 man_pred[1:e_terms]=study_var[1:e_terms]
for (i in (e_terms+1):length(study_var)){
  e_1=study_var[i-1]-man_pred[i-1]; if (sum(e_1)==0) e_1=0 else if (is.na(e_1)) e_1=0
  e_2=study_var[i-2]-man_pred[i-2]; if (sum(e_2)==0) e_2=0 else if (is.na(e_2)) e_2=0
  ma_part=ma1*e_1+ma2*e_2
  
  exo_part=Airings_coef*(Airings[i]-Airings[i-1]-ar1*(Airings[i-1]-Airings[i-2]))
  
  ar_part=study_var[i-1]+ar1*(study_var[i-1]-study_var[i-2])
  
  man_pred[i]=ar_part+ma_part+exo_part
}

  man_pred[1:20]
  fitted(Airings_arima)[1:20]
lim_max=max(max(man_pred,na.rm=TRUE),max(fitted(Airings_arima),na.rm=TRUE))
lim_min=min(min(man_pred,na.rm=TRUE),min(fitted(Airings_arima),na.rm=TRUE))
qplot(man_pred,fitted(Airings_arima),xlim=c(lim_min,lim_max),ylim=c(lim_min,lim_max))
man_fit=lm(man_pred~fitted(Airings_arima))
summary(man_fit)
coef(man_fit)


```





```{r echo=FALSE, message=FALSE}

qplot(study_var,fitted(stepwise_model))+theme_bw()+ggtitle("Stepwise Polynomial Fit")+
  xlab(paste(title_paste,"Sessions"))+ylab("Fitted Values")
qplot(study_var,as.vector(fitted(Airings_arima)))+theme_bw()+ggtitle("ARIMAX Fit")+
  xlab(paste(title_paste,"Sessions"))+ylab("Fitted Values")

```

## Organic Home Channel

```{r echo=FALSE, message=FALSE}
study_var=channel_sessions_long$organic.home
na_inds=which(is.na(study_var))
Airings=channel_sessions_long$Airings[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="Organic Home"
```

###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be 52 (weeks per year), but we don't have two full periods

poly_fit=lm(study_var~Airings+I(Airings^2))
tmp_df=data.frame(round(coef(poly_fit),3))
tmp_df=rbind(tmp_df,cor(fitted(poly_fit),na.omit(study_var))^2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
pander(tmp_df)

```


###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
big_poly_fit=lm(study_var~Airings+I(Airings^2)+I(Airings^3)+I(Airings^4))
stepwise_model=step(big_poly_fit,k=log(nrow(channel_sessions_long)),scope = list(lower = ~Airings))
```

```{r echo=FALSE, message=FALSE}
tmp_df=data.frame(round(coef(stepwise_model),3))
tmp_df=rbind(tmp_df,cor(fitted(stepwise_model),na.omit(study_var))^2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
pander(tmp_df)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
tmp_df=data.frame(Airings=Airings,channel=study_var,poly=fitted(poly_fit),
                  step=fitted(stepwise_model))
ggplot(tmp_df) + theme_bw()+
  geom_point(aes(x=Airings,y=channel,color=title_paste))+ 
  geom_line(aes(x=Airings,y=poly,color="2nd Order Plynomial Fit"))+ 
  geom_line(aes(x=Airings,y=step,color="Stepwise Polynomial Fit"))+ 
  ggtitle("Model Fits")+xlab("Airings Speding (Dollars)")+ylab("Sessions")+
  guides(color=guide_legend(title="Models"))

#This plot shows a major time trend component- implying previous models were useless
t=Box.test(stepwise_model$residuals)
box_p=round(t$p.value,4)
qplot(channel_sessions_long$date[-na_inds],stepwise_model$residuals)+theme_bw()+
  ggtitle(paste("Polynomial Fit Residuals, Box Test p-value",box_p) )+xlab("Date")+ylab("Residuals")


```

###Trend Decomposition

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
ts_var=ts(study_var, frequency = 365)
stl_obj=stl(ts_var, s.window="periodic",robust=TRUE)
plot(stl_obj)+title(paste(title_paste,"Seasonal Trend Decomposition"))

qplot(date,Airings)+theme_bw()+ggtitle("Airings")+xlab("Date")+ylab("Dollars")

stl_residuals=stl_obj$time.series[,3]

temp_df=data.frame(Airings,stl_residuals)
ggplot(temp_df,aes(x=Airings,y=stl_residuals))+theme_bw()+
  geom_smooth(method="lm")+geom_point()+ggtitle("Airings Against Smoothed Residuals")+xlab("Dollars")+ylab("Residuals")

```


```{r echo=FALSE, message=FALSE, warning=FALSE}
 new_r2=round(cor(Airings,stl_residuals),2)
 old_r2=round(cor(Airings,study_var),2)
 temp_df=data.frame(Message=c("Orignal Correlation:","Residuals Correlation:"),R2=c(old_r2,new_r2))
 pander(temp_df)

```


###ARIMAX model with Airings spend

```{r echo=FALSE, message=FALSE, warning=FALSE}

#Not allowing for seasonal component until we have two years of data
Airings_arima=auto.arima(study_var,xreg=c(Airings),max.P=0,max.D = 0,max.Q = 0,allowdrift=FALSE,allowmean = FALSE)
 # Airings_arima=auto.arima(study_var,xreg=c(Airings),allowdrift=FALSE,allowmean = FALSE)

arima_formula(Airings_arima,Airings)
# Airings_arima_fcast=forecast(Airings_arima,xreg=c(Airings),1)
# plot(Airings_arima_fcast)


#Building coefficient and R2 table
Airings_arima_R2=round(cor(fitted(Airings_arima),ts_var)^2,2)
tmp_df=data.frame(coef(Airings_arima))
tmp_df=rbind(tmp_df,Airings_arima_R2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
pander(tmp_df)

```


```{r echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
#Secret manual modeling
##Attempting to build the arim simple enough for excel
#for (3,0,0) model
ar1=coef(Airings_arima)[grep("ar1",names(coef(Airings_arima)))]
ar2=coef(Airings_arima)[grep("ar2",names(coef(Airings_arima)))]
ar3=coef(Airings_arima)[grep("ar3",names(coef(Airings_arima)))]

Airings_coef=coef(Airings_arima)[grep("Airings",names(coef(Airings_arima)))]
 

e_terms=3
 man_pred=rep(NA,length(study_var))
 man_pred[1:e_terms]=study_var[1:e_terms]
for (i in (e_terms+1):length(ts_var)){
  
  exo_part=Airings_coef*(Airings[i]-ar1*Airings[i-1]-ar2*Airings[i-2]-ar3*Airings[i-3])
  
  ar_part=ar1*ts_var[i-1]+ar2*ts_var[i-2]+ar3*ts_var[i-3]
  
  man_pred[i]=ar_part+exo_part
}

  man_pred[1:20]
  fitted(Airings_arima)[1:20]
lim_max=max(max(man_pred,na.rm=TRUE),max(fitted(Airings_arima),na.rm=TRUE))
lim_min=min(min(man_pred,na.rm=TRUE),min(fitted(Airings_arima),na.rm=TRUE))
qplot(man_pred,fitted(Airings_arima),xlim=c(lim_min,lim_max),ylim=c(lim_min,lim_max))
man_fit=lm(man_pred~fitted(Airings_arima))
summary(man_fit)
coef(man_fit)


```


```{r echo=FALSE, message=FALSE}

qplot(study_var,fitted(stepwise_model))+theme_bw()+ggtitle("Stepwise Polynomial Fit")+
  xlab(paste(title_paste,"Sessions"))+ylab("Fitted Values")
qplot(study_var,as.vector(fitted(Airings_arima)))+theme_bw()+ggtitle("ARIMAX Fit")+
  xlab(paste(title_paste,"Sessions"))+ylab("Fitted Values")

```


## Direct Net Home Channel

```{r echo=FALSE, message=FALSE}
study_var=channel_sessions_long$direct.net.home
na_inds=which(is.na(study_var))
Airings=channel_sessions_long$Airings[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="Direct Net Home"
```

###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be 52 (weeks per year), but we don't have two full periods

poly_fit=lm(study_var~Airings+I(Airings^2))
tmp_df=data.frame(round(coef(poly_fit),3))
tmp_df=rbind(tmp_df,cor(fitted(poly_fit),na.omit(study_var))^2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
pander(tmp_df)

```


###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
big_poly_fit=lm(study_var~Airings+I(Airings^2)+I(Airings^3)+I(Airings^4))
stepwise_model=step(big_poly_fit,k=log(nrow(channel_sessions_long)),scope = list(lower = ~Airings))
```

```{r echo=FALSE, message=FALSE}
tmp_df=data.frame(round(coef(stepwise_model),3))
tmp_df=rbind(tmp_df,cor(fitted(stepwise_model),na.omit(study_var))^2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
pander(tmp_df)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
tmp_df=data.frame(Airings=Airings,channel=study_var,poly=fitted(poly_fit),
                  step=fitted(stepwise_model))
ggplot(tmp_df) + theme_bw()+
  geom_point(aes(x=Airings,y=channel,color=title_paste))+ 
  geom_line(aes(x=Airings,y=poly,color="2nd Order Plynomial Fit"))+ 
  geom_line(aes(x=Airings,y=step,color="Stepwise Polynomial Fit"))+ 
  ggtitle("Model Fits")+xlab("Airings Speding (Dollars)")+ylab("Sessions")+
  guides(color=guide_legend(title="Models"))

#This plot shows a major time trend component- implying previous models were useless
t=Box.test(stepwise_model$residuals)
box_p=round(t$p.value,4)
qplot(channel_sessions_long$date[-na_inds],stepwise_model$residuals)+theme_bw()+
  ggtitle(paste("Polynomial Fit Residuals, Box Test p-value",box_p) )+xlab("Date")+ylab("Residuals")


```

###Trend Decomposition

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
ts_var=ts(study_var, frequency = 365)
stl_obj=stl(ts_var, s.window="periodic",robust=TRUE)
plot(stl_obj)+title(paste(title_paste,"Seasonal Trend Decomposition"))

qplot(date,Airings)+theme_bw()+ggtitle("Airings")+xlab("Date")+ylab("Dollars")

stl_residuals=stl_obj$time.series[,3]

temp_df=data.frame(Airings,stl_residuals)
ggplot(temp_df,aes(x=Airings,y=stl_residuals))+theme_bw()+
  geom_smooth(method="lm")+geom_point()+ggtitle("Airings Against Smoothed Residuals")+xlab("Dollars")+ylab("Residuals")

```



```{r echo=FALSE, message=FALSE, warning=FALSE}
 new_r2=round(cor(Airings,stl_residuals),2)
 old_r2=round(cor(Airings,study_var),2)
 temp_df=data.frame(Message=c("Orignal Correlation:","Residuals Correlation:"),R2=c(old_r2,new_r2))
 pander(temp_df)

```


###ARIMAX model with Airings spend

```{r echo=FALSE, message=FALSE, warning=FALSE}

#Not allowing for seasonal component until we have two years of data
Airings_arima=auto.arima(study_var,xreg=c(Airings),max.P=0,max.D = 0,max.Q = 0,allowdrift=FALSE,allowmean = FALSE)
 # Airings_arima=auto.arima(study_var,xreg=c(Airings),allowdrift=FALSE,allowmean = FALSE)
arima_formula(Airings_arima,Airings)
# Airings_arima_fcast=forecast(Airings_arima,xreg=c(Airings),h=0)
# plot(Airings_arima_fcast)



#Building coefficient and R2 table
Airings_arima_R2=round(cor(fitted(Airings_arima),ts_var)^2,2)
tmp_df=data.frame(coef(Airings_arima))
tmp_df=rbind(tmp_df,Airings_arima_R2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
pander(tmp_df)

```


```{r echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
#Secret manual modeling
##Attempting to build the arim simple enough for excel
#for (3,0,0) model
ar1=coef(Airings_arima)[grep("ar1",names(coef(Airings_arima)))]
ar2=coef(Airings_arima)[grep("ar2",names(coef(Airings_arima)))]
ar3=coef(Airings_arima)[grep("ar3",names(coef(Airings_arima)))]

Airings_coef=coef(Airings_arima)[grep("Airings",names(coef(Airings_arima)))]
 

e_terms=3
 man_pred=rep(NA,length(study_var))
 man_pred[1:e_terms]=study_var[1:e_terms]
for (i in (e_terms+1):length(study_var)){
  
  exo_part=Airings_coef*(Airings[i]-ar1*Airings[i-1]-ar2*Airings[i-2]-ar3*Airings[i-3])
  
  ar_part=ar1*study_var[i-1]+ar2*study_var[i-2]+ar3*study_var[i-3]
  
  man_pred[i]=ar_part+exo_part
}

  man_pred[1:20]
  fitted(Airings_arima)[1:20]
lim_max=max(max(man_pred,na.rm=TRUE),max(fitted(Airings_arima),na.rm=TRUE))
lim_min=min(min(man_pred,na.rm=TRUE),min(fitted(Airings_arima),na.rm=TRUE))
qplot(man_pred,fitted(Airings_arima),xlim=c(lim_min,lim_max),ylim=c(lim_min,lim_max))
man_fit=lm(man_pred~fitted(Airings_arima))
summary(man_fit)
coef(man_fit)


```



```{r echo=FALSE, message=FALSE}

qplot(study_var,fitted(stepwise_model))+theme_bw()+ggtitle("Stepwise Polynomial Fit")+
  xlab(paste(title_paste,"Sessions"))+ylab("Fitted Values")
qplot(study_var,as.vector(fitted(Airings_arima)))+theme_bw()+ggtitle("ARIMAX Fit")+
  xlab(paste(title_paste,"Sessions"))+ylab("Fitted Values")

```

## Direcy Home Channel

```{r echo=FALSE, message=FALSE}
study_var=channel_sessions_long$direct.home
na_inds=which(is.na(study_var))
Airings=channel_sessions_long$Airings[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="Direct Home"
```

###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be 52 (weeks per year), but we don't have two full periods
poly_fit=lm(study_var~Airings+I(Airings^2))
tmp_df=data.frame(round(coef(poly_fit),3))
tmp_df=rbind(tmp_df,cor(fitted(poly_fit),na.omit(study_var))^2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
pander(tmp_df)

```


###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
big_poly_fit=lm(study_var~Airings+I(Airings^2)+I(Airings^3)+I(Airings^4))
stepwise_model=step(big_poly_fit,k=log(nrow(channel_sessions_long)),scope = list(lower = ~Airings))
```

```{r echo=FALSE, message=FALSE}
tmp_df=data.frame(round(coef(stepwise_model),3))
tmp_df=rbind(tmp_df,cor(fitted(stepwise_model),na.omit(study_var))^2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
pander(tmp_df)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
tmp_df=data.frame(Airings=Airings,channel=study_var,poly=fitted(poly_fit),
                  step=fitted(stepwise_model))
ggplot(tmp_df) + theme_bw()+
  geom_point(aes(x=Airings,y=channel,color=title_paste))+ 
  geom_line(aes(x=Airings,y=poly,color="2nd Order Plynomial Fit"))+ 
  geom_line(aes(x=Airings,y=step,color="Stepwise Polynomial Fit"))+ 
  ggtitle("Model Fits")+xlab("Airings Speding (Dollars)")+ylab("Sessions")+
  guides(color=guide_legend(title="Models"))

#This plot shows a major time trend component- implying previous models were useless
t=Box.test(stepwise_model$residuals)
box_p=round(t$p.value,4)
qplot(channel_sessions_long$date[-na_inds],stepwise_model$residuals)+theme_bw()+
  ggtitle(paste("Polynomial Fit Residuals, Box Test p-value",box_p) )+xlab("Date")+ylab("Residuals")



```

###Trend Decomposition

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
ts_var=ts(study_var, frequency = 365)
stl_obj=stl(ts_var, s.window="periodic",robust=TRUE)
plot(stl_obj)+title(paste(title_paste,"Seasonal Trend Decomposition"))

qplot(date,Airings)+theme_bw()+ggtitle("Airings")+xlab("Date")+ylab("Dollars")

stl_residuals=stl_obj$time.series[,3]

temp_df=data.frame(Airings,stl_residuals)
ggplot(temp_df,aes(x=Airings,y=stl_residuals))+theme_bw()+
  geom_smooth(method="lm")+geom_point()+ggtitle("Airings Against Smoothed Residuals")+xlab("Dollars")+ylab("Residuals")

```


```{r echo=FALSE, message=FALSE, warning=FALSE}
 new_r2=round(cor(Airings,stl_residuals),2)
 old_r2=round(cor(Airings,study_var),2)
 temp_df=data.frame(Message=c("Orignal Correlation:","Residuals Correlation:"),R2=c(old_r2,new_r2))
 pander(temp_df)

```


###ARIMAX model with Airings spend

```{r echo=FALSE, message=FALSE, warning=FALSE}


#Not allowing for seasonal component until we have two years of data
Airings_arima=auto.arima(study_var,xreg=c(Airings),max.P=0,max.D = 0,max.Q = 0,allowdrift=FALSE,allowmean = FALSE)
 # Airings_arima=auto.arima(study_var,xreg=c(Airings),allowdrift=FALSE,allowmean = FALSE)
arima_formula(Airings_arima,Airings)
# Airings_arima_fcast=forecast(Airings_arima,xreg=c(Airings),h=0)
# plot(Airings_arima_fcast)



#Building coefficient and R2 table
Airings_arima_R2=round(cor(fitted(Airings_arima),ts_var)^2,2)
tmp_df=data.frame(coef(Airings_arima))
tmp_df=rbind(tmp_df,Airings_arima_R2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
pander(tmp_df)

```


```{r echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
#Secret manual modeling
##Attempting to build the arim simple enough for excel
#for (1,0,0) model

ar1=coef(Airings_arima)[grep("ar1",names(coef(Airings_arima)))]
Airings_coef=coef(Airings_arima)[grep("Airings",names(coef(Airings_arima)))]
 

e_terms=1
 man_pred=rep(NA,length(study_var))
 man_pred[1:e_terms]=study_var[1:e_terms]
for (i in (e_terms+1):length(study_var)){
  
  exo_part=Airings_coef*(Airings[i]-ar1*Airings[i-1])
  
  ar_part=ar1*ts_var[i-1]
  
  man_pred[i]=ar_part+exo_part
}

  man_pred[1:20]
  fitted(Airings_arima)[1:20]
lim_max=max(max(man_pred,na.rm=TRUE),max(fitted(Airings_arima),na.rm=TRUE))
lim_min=min(min(man_pred,na.rm=TRUE),min(fitted(Airings_arima),na.rm=TRUE))
qplot(man_pred,fitted(Airings_arima),xlim=c(lim_min,lim_max),ylim=c(lim_min,lim_max))
man_fit=lm(man_pred~fitted(Airings_arima))
summary(man_fit)
coef(man_fit)


```


```{r echo=FALSE, message=FALSE}

qplot(study_var,fitted(stepwise_model))+theme_bw()+ggtitle("Stepwise Polynomial Fit")+
  xlab(paste(title_paste,"Sessions"))+ylab("Fitted Values")
qplot(study_var,as.vector(fitted(Airings_arima)))+theme_bw()+ggtitle("ARIMAX Fit")+
  xlab(paste(title_paste,"Sessions"))+ylab("Fitted Values")

```


## Paid Brand Channel

```{r echo=FALSE, message=FALSE}
study_var=channel_sessions_long$paid.brand.sessions
na_inds=which(is.na(study_var))
Airings=channel_sessions_long$Airings[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="Paid Brand"
```

###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}

poly_fit=lm(study_var~Airings+I(Airings^2))
tmp_df=data.frame(round(coef(poly_fit),3))
tmp_df=rbind(tmp_df,cor(fitted(poly_fit),na.omit(study_var))^2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
pander(tmp_df)

```


###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
big_poly_fit=lm(study_var~Airings+I(Airings^2)+I(Airings^3)+I(Airings^4))
stepwise_model=step(big_poly_fit,k=log(nrow(channel_sessions_long)),scope = list(lower = ~Airings))
```

```{r echo=FALSE, message=FALSE}
tmp_df=data.frame(round(coef(stepwise_model),3))
tmp_df=rbind(tmp_df,cor(fitted(stepwise_model),na.omit(study_var))^2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
pander(tmp_df)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
tmp_df=data.frame(Airings=Airings,channel=study_var,poly=fitted(poly_fit),
                  step=fitted(stepwise_model))
ggplot(tmp_df) + theme_bw()+
  geom_point(aes(x=Airings,y=channel,color=title_paste))+ 
  geom_line(aes(x=Airings,y=poly,color="2nd Order Plynomial Fit"))+ 
  geom_line(aes(x=Airings,y=step,color="Stepwise Polynomial Fit"))+ 
  ggtitle("Model Fits")+xlab("Airings Speding (Dollars)")+ylab("Sessions")+
  guides(color=guide_legend(title="Models"))

#This plot shows a major time trend component- implying previous models were useless
t=Box.test(stepwise_model$residuals)
box_p=round(t$p.value,4)
qplot(channel_sessions_long$date[-na_inds],stepwise_model$residuals)+theme_bw()+
  ggtitle(paste("Polynomial Fit Residuals, Box Test p-value",box_p) )+xlab("Date")+ylab("Residuals")

```


###Trend Decomposition

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
#frequency shoud be 52 (weeks per year), but we don't have two full periods
ts_var=ts(study_var, frequency = 365)
stl_obj=try(stl(ts_var, s.window="periodic",robust=TRUE))
if (class(stl_obj)=="try-error") {
  ts_var=ts(study_var, frequency = 183)
  stl_obj=stl(ts_var, s.window="periodic",robust=TRUE)
}
  plot(stl_obj)+title(paste(title_paste,"Seasonal Trend Decomposition"))


qplot(date,Airings)+theme_bw()+ggtitle("Airings")+xlab("Date")+ylab("Dollars")

stl_residuals=stl_obj$time.series[,3]

temp_df=data.frame(Airings,stl_residuals)
ggplot(temp_df,aes(x=Airings,y=stl_residuals))+theme_bw()+
  geom_smooth(method="lm")+geom_point()+ggtitle("Airings Against Smoothed Residuals")+xlab("Dollars")+ylab("Residuals")
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
 new_r2=round(cor(Airings,stl_residuals),2)
 old_r2=round(cor(Airings,study_var),2)
 temp_df=data.frame(Message=c("Orignal Correlation:","Residuals Correlation:"),R2=c(old_r2,new_r2))
 pander(temp_df)

```




###ARIMAX model with Airings spend

```{r echo=FALSE, message=FALSE, warning=FALSE}

#Not allowing for seasonal component until we have two years of data
Airings_arima=auto.arima(study_var,xreg=c(Airings),max.P=0,max.D = 0,max.Q = 0,allowdrift=FALSE,allowmean = FALSE)
 # Airings_arima=auto.arima(study_var,xreg=c(Airings),allowdrift=FALSE,allowmean = FALSE)

arima_formula(Airings_arima,Airings)
# Airings_arima_fcast=forecast(Airings_arima,xreg=c(Airings),h=0)
# plot(Airings_arima_fcast)



#Building coefficient and R2 table
Airings_arima_R2=round(cor(fitted(Airings_arima),ts_var)^2,2)
tmp_df=data.frame(coef(Airings_arima))
tmp_df=rbind(tmp_df,Airings_arima_R2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
pander(tmp_df)

```


```{r echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
#Secret manual modeling
##Attempting to build the arim simple enough for excel
#for (1,1,1) model
ma1=coef(Airings_arima)[grep("ma1",names(coef(Airings_arima)))]
ar1=coef(Airings_arima)[grep("ar1",names(coef(Airings_arima)))]
Airings_coef=coef(Airings_arima)[grep("Airings",names(coef(Airings_arima)))]
 

e_terms=2
 man_pred=rep(NA,length(study_var))
 man_pred[1:e_terms]=study_var[1:e_terms]
for (i in (e_terms+1):length(study_var)){
  e_1=study_var[i-1]-man_pred[i-1]; if (sum(e_1)==0) e_1=0 else if (is.na(e_1)) e_1=0
  ma_part=ma1*e_1
  
  exo_part=Airings_coef*(Airings[i]-Airings[i-1]-ar1*(Airings[i-1]-Airings[i-2]))
  
  ar_part=study_var[i-1]+ar1*(study_var[i-1]-study_var[i-2])
  
  man_pred[i]=ar_part+ma_part+exo_part
}

  man_pred[1:20]
  fitted(Airings_arima)[1:20]
lim_max=max(max(man_pred,na.rm=TRUE),max(fitted(Airings_arima),na.rm=TRUE))
lim_min=min(min(man_pred,na.rm=TRUE),min(fitted(Airings_arima),na.rm=TRUE))
qplot(man_pred,fitted(Airings_arima),xlim=c(lim_min,lim_max),ylim=c(lim_min,lim_max))
man_fit=lm(man_pred~fitted(Airings_arima))
summary(man_fit)
coef(man_fit)


```


```{r echo=FALSE, message=FALSE}


qplot(study_var,fitted(stepwise_model))+theme_bw()+ggtitle("Stepwise Polynomial Fit")+
  xlab(paste(title_paste,"Sessions"))+ylab("Fitted Values")
qplot(study_var,as.vector(fitted(Airings_arima)))+theme_bw()+ggtitle("ARIMAX Fit")+
  xlab(paste(title_paste,"Sessions"))+ylab("Fitted Values")

```
