---
title: "TV Channel Models old tv vendor"
output: html_document
---

```{r echo=FALSE, message=FALSE, warning=FALSE} 
library(tidyr)
library(dplyr)
library(openxlsx)
library(lubridate)
library(ggplot2)
library(gridExtra)
library(forecast)
library(stats)
library(pander)
library(TTR)
library(googlesheets)

source("report_functions.R")

```



```{r echo=FALSE, message=FALSE}
load(file="channel_sessions_long.rda")
freq=52

```


```{r echo=FALSE, message=FALSE, warning=FALSE}
channel_session_gathered=channel_sessions_long %>% gather(key=channel,value=sessions,2:6)
channel_session_gathered$Units="Sessions"
channel_session_gathered$Units[which(channel_session_gathered$channel=="tv.spend")]="Dollars"

ggplot(channel_session_gathered)+theme_bw()+
  geom_line(aes(x=date,y=sessions,color=channel))+
  facet_grid(Units~.,scales="free")+ylab("")+xlab("Date")+
  ggtitle("Weekly TV Spending And Channel Sessions")


```

```{r echo=FALSE, message=FALSE, warning=FALSE}
vars<-c("organic.net.home","organic.home","direct.net.home","direct.home","paid.brand.sessions")
#always sort by descending date first!!
ccf.df=data.frame(Correlation=NULL,Lag=NULL,Source=NULL)
for (var in vars) {
  ind=which(names(channel_sessions_long) == var)
  study_var=channel_sessions_long[,ind]
  na_inds=which(is.na(study_var))
  tv=channel_sessions_long$tv.spend[-na_inds]
  study_var=na.omit(study_var)
  
  
  ccf_temp<-ccf(tv,study_var,plot=FALSE)
  ccf_temp_df=data.frame(Correlation=ccf_temp$acf,Lag=ccf_temp$lag,Source=rep(var,length(ccf_temp$lag)))
  
  ccf.df<-rbind(ccf.df,ccf_temp_df)
}

CCF_plot<-ggplot(ccf.df %>% filter(Lag>=0),aes(x=Lag,y=Correlation,color=Source))+ theme_bw()+
  geom_point()+ggtitle("TV Spending Delayed Effect")+xlab("Lag (Weeks)")+
  scale_color_manual( values=rainbow(length(vars)),
                      name="Source",
                      breaks=vars,
                      labels=vars)
CCF_plot
```

## Organic Net Home Channel

```{r echo=FALSE, message=FALSE}
var_name="organic.net.home"
study_var=channel_sessions_long[,which(names(channel_sessions_long)==var_name)][[1]]

na_inds=which(is.na(study_var))
tv=channel_sessions_long$tv.spend[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]
title_paste="Organic Net Home"

```

###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be freq (weeks per year), but we don't have two full periods
poly_fit=report_poly_fit_2(study_var,tv)
report_poly_fit_2_sub(poly_fit,study_var)
```


###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
stepwise_model=step_model(study_var,tv)
```

```{r echo=FALSE, message=FALSE}
step_pander(stepwise_model)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

poly_plots(tv,study_var,poly_fit,stepwise_model)

```

###Trend Decomposition

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
stl_func(study_var,freq)

```



###ARIMAX model with TV spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
tv_arima=arima_func(stepwise_model,study_var,tv,freq)
arima_func_sub(tv_arima,stepwise_model,study_var,tv,freq)

```


```{r echo=FALSE, message=FALSE}

# model_comp_plots(stepwise_model,tv_arima)
transformed_plot(tv_arima,tv)

```


###Forecasts

```{r echo=FALSE, message=FALSE, warning=FALSE}
channel_sessions_long=add_forecast_to_df(channel_sessions_long,tv_arima,var_name)



channel_sessions_long=channel_sessions_long %>% rename(organic.net.home.forecast=forecast) 
   # plot(channel_sessions_long$organic.net.home.forecast)
   # lines(study_var)

```  

###Model Validation
```{r echo=FALSE, message=FALSE, warning=FALSE}
model_validation(tv_arima,study_var,tv,freq,date)

```


## Organic Home Channel

```{r echo=FALSE, message=FALSE}
var_name="organic.home"
study_var=channel_sessions_long[,which(names(channel_sessions_long)==var_name)][[1]]


na_inds=which(is.na(study_var))
tv=channel_sessions_long$tv.spend[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="Organic Home"
```

###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be freq (weeks per year), but we don't have two full periods
poly_fit=report_poly_fit_2(study_var,tv)
report_poly_fit_2_sub(poly_fit,study_var)
```


###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
stepwise_model=step_model(study_var,tv)
```

```{r echo=FALSE, message=FALSE}
step_pander(stepwise_model)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

poly_plots(tv,study_var,poly_fit,stepwise_model)

```

###Trend Decomposition

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
stl_func(study_var,freq)

```



###ARIMAX model with TV spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
tv_arima=arima_func(stepwise_model,study_var,tv,freq)
arima_func_sub(tv_arima,stepwise_model,study_var,tv,freq)

```


```{r echo=FALSE, message=FALSE}

# model_comp_plots(stepwise_model,tv_arima)
transformed_plot(tv_arima,tv)

```


###Forecasts

```{r echo=FALSE, message=FALSE, warning=FALSE}
channel_sessions_long=add_forecast_to_df(channel_sessions_long,tv_arima,var_name)


channel_sessions_long=channel_sessions_long %>% rename(organic.home.forecast=forecast) 
   # plot(channel_sessions_long$organic.net.home.forecast)
   # lines(study_var)

```  

###Model Validation
```{r echo=FALSE, message=FALSE, warning=FALSE}
model_validation(tv_arima,study_var,tv,freq,date)
```



## Direct Net Home Channel

```{r echo=FALSE, message=FALSE}
var_name="direct.net.home"
study_var=channel_sessions_long[,which(names(channel_sessions_long)==var_name)][[1]]


na_inds=which(is.na(study_var))
tv=channel_sessions_long$tv.spend[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="Direct Net Home"
```


###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be freq (weeks per year), but we don't have two full periods
poly_fit=report_poly_fit_2(study_var,tv)
report_poly_fit_2_sub(poly_fit,study_var)
```


###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
stepwise_model=step_model(study_var,tv)
```

```{r echo=FALSE, message=FALSE}
step_pander(stepwise_model)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

poly_plots(tv,study_var,poly_fit,stepwise_model)

```

###Trend Decomposition

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
stl_func(study_var,freq)

```



###ARIMAX model with TV spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
tv_arima=arima_func(stepwise_model,study_var,tv,freq)
arima_func_sub(tv_arima,stepwise_model,study_var,tv,freq)

```


```{r echo=FALSE, message=FALSE}

# model_comp_plots(stepwise_model,tv_arima)
transformed_plot(tv_arima,tv)

```


###Forecasts

```{r echo=FALSE, message=FALSE, warning=FALSE}
channel_sessions_long=add_forecast_to_df(channel_sessions_long,tv_arima,var_name)


channel_sessions_long=channel_sessions_long %>% rename(direct.net.home.forecast=forecast) 
   # plot(channel_sessions_long$organic.net.home.forecast)
   # lines(study_var)

```  


###Model Validation
```{r echo=FALSE, message=FALSE, warning=FALSE}
model_validation(tv_arima,study_var,tv,freq,date)
```


## Direct Home Channel

```{r echo=FALSE, message=FALSE}
var_name="direct.home"
study_var=channel_sessions_long[,which(names(channel_sessions_long)==var_name)][[1]]

na_inds=which(is.na(study_var))
tv=channel_sessions_long$tv.spend[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="Direct Home"
```

###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be freq (weeks per year), but we don't have two full periods
poly_fit=report_poly_fit_2(study_var,tv)
report_poly_fit_2_sub(poly_fit,study_var)
```


###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
stepwise_model=step_model(study_var,tv)
```

```{r echo=FALSE, message=FALSE}
step_pander(stepwise_model)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

poly_plots(tv,study_var,poly_fit,stepwise_model)

```

###Trend Decomposition

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
stl_func(study_var,freq)

```



###ARIMAX model with TV spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
tv_arima=arima_func(stepwise_model,study_var,tv,freq)
arima_func_sub(tv_arima,stepwise_model,study_var,tv,freq)

```


```{r echo=FALSE, message=FALSE}

# model_comp_plots(stepwise_model,tv_arima)
transformed_plot(tv_arima,tv)
```


###Forecasts

```{r echo=FALSE, message=FALSE, warning=FALSE}
channel_sessions_long=add_forecast_to_df(channel_sessions_long,tv_arima,var_name)


channel_sessions_long=channel_sessions_long %>% rename(direct.home.forecast=forecast) 
   # plot(channel_sessions_long$organic.net.home.forecast)
   # lines(study_var)

```  

###Model Validation
```{r echo=FALSE, message=FALSE, warning=FALSE}
model_validation(tv_arima,study_var,tv,freq,date)
```


## Paid Brand Channel

```{r echo=FALSE, message=FALSE}
var_name="paid.brand.sessions"
study_var=channel_sessions_long[,which(names(channel_sessions_long)==var_name)][[1]]
na_inds=which(is.na(study_var))
tv=channel_sessions_long$tv.spend[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="Paid Brand"
```

###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be freq (weeks per year), but we don't have two full periods
poly_fit=report_poly_fit_2(study_var,tv)
report_poly_fit_2_sub(poly_fit,study_var)
```


###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
stepwise_model=step_model(study_var,tv)
```

```{r echo=FALSE, message=FALSE}
step_pander(stepwise_model)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

poly_plots(tv,study_var,poly_fit,stepwise_model)

```

###Trend Decomposition

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
stl_func(study_var,freq)

```



###ARIMAX model with TV spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
tv_arima=arima_func(stepwise_model,study_var,tv,freq)
arima_func_sub(tv_arima,stepwise_model,study_var,tv,freq)

```


```{r echo=FALSE, message=FALSE}

# model_comp_plots(stepwise_model,tv_arima)
transformed_plot(tv_arima,tv)

```


###Forecasts

```{r echo=FALSE, message=FALSE, warning=FALSE}
channel_sessions_long=add_forecast_to_df(channel_sessions_long,tv_arima,var_name)


channel_sessions_long=channel_sessions_long %>% rename(paid.brand.sessions.forecast=forecast) 
   # plot(channel_sessions_long$organic.net.home.forecast)
   # lines(study_var)

```  


###Model Validation
There are not enough data points to perform model validation for this channel
```{r echo=FALSE, message=FALSE, warning=FALSE}

# model_validation(tv_arima,study_var,tv,freq,date)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# write.csv(channel_sessions_long,file="channel_sessions_long_with_forecasts.csv")
# gs_upload("channel_sessions_long_with_forecasts.csv",sheet_title = "weekly_tv_channel_with_forecasts_upload_dont_edit")

```

