---
title: "TV Spending Impact on Site Visits"
output: html_document
---

#Synopsis

This report explores how investing in TV advertising affects site visits. The report will look into seven primary sources of site traffic: organic net of home, organic home, organic all, direct net of home, direct home, direct all, and paid brand. A time-series model will be fit for each channel. This will allow us to isolate the effect of tv spending on site visits from the natural trend of those channels had no spending occured. The tv spending contribution will be considered the directionally accurate lift effect.

```{r echo=FALSE, message=FALSE, warning=FALSE} 
library(tidyr)
library(dplyr)
library(openxlsx)
library(lubridate)
library(ggplot2)
library(gridExtra)
library(forecast)
library(stats)
library(pander)
library(TTR)
library(googlesheets)
library(zoo)

source("report_functions.R")

```



```{r echo=FALSE, message=FALSE}
load(file="channel_sessions_long.rda")
# source("tv_channel_models_data_munge.R")
freq=52

#Pretending Comcast never happened
# comcast_switch_date="2015-05-04"
# adap_switch_date="2015-09-14"
# comcast_ind=which(channel_sessions_long$date>comcast_switch_date & channel_sessions_long$date<adap_switch_date)
# channel_sessions_long$tv.spend[comcast_ind]=0

```

#Exploration

This graph plots tv spending, gross merchandising value, and sites visits by channel over time.


```{r echo=FALSE, message=FALSE, warning=FALSE}
channel_sessions_long$GMV=channel_sessions_long$GMV/(10^6)
channel_session_gathered=channel_sessions_long %>% gather(key=channel,value=sessions,2:10)
channel_session_gathered$Units="Sessions"
channel_session_gathered$Units[which(channel_session_gathered$channel=="tv.spend")]="TV (Dollars)"
channel_session_gathered$Units[which(channel_session_gathered$channel=="GMV")]="GMV (10^6 Dollars)"
# levels(channel_session_gathered$channel)

ggplot(channel_session_gathered)+theme_bw()+
  geom_line(aes(x=date,y=sessions,color=channel))+
  facet_grid(Units~.,scales="free")+ylab("")+xlab("Date")+
  ggtitle("Weekly TV Spending And Channel Sessions")+
   theme(legend.title=element_blank())+
  scale_color_manual(values=rainbow(9),
                     labels=c("GMV","TV Spending","Direct All","Direct Net of Home","Direct Home",
                              "Organic Net of Home","Organic All","Organic Home","Paid Brand"))
  


```

The graph below illustrates the residual effects of money spent on TV advertising on other variables. The points at lag 0 represent the direct correlation. The points at lag 1 represent represent the correlation of TV spending and the compared variable one week later and so on. At the weekly level we can see that the greatest relationship occurs with no lag element 

```{r echo=FALSE, message=FALSE, warning=FALSE}
vars<-c("organic.net.home","organic.home","organic.all","direct.net.home","direct.home","direct.all","paid.brand","GMV")
#always sort by ascending date first!!
ccf.df=data.frame(Correlation=NULL,Lag=NULL,Source=NULL)
for (var in vars) {
  ind=which(names(channel_sessions_long) == var)
  study_var=channel_sessions_long[,ind]
  na_inds=which(is.na(study_var))
  tv=channel_sessions_long$tv.spend[-na_inds]
  study_var=na.omit(study_var)
  
  
  ccf_temp<-ccf(tv,study_var,plot=FALSE)
  ccf_temp_df=data.frame(Correlation=ccf_temp$acf,Lag=ccf_temp$lag,Source=rep(var,length(ccf_temp$lag)))
  
  ccf.df<-rbind(ccf.df,ccf_temp_df)
}

ggplot(ccf.df %>% filter(Lag>=0),aes(x=Lag,y=Correlation,color=Source))+ theme_bw()+
  geom_point()+ggtitle("TV Spending Delayed Effect")+xlab("Lag (Weeks)")+
  scale_color_manual( values=rainbow(length(vars)),
                      name="Source",
                      breaks=vars,
                      labels=c("Organic Net of Home","Organic Home","Organic All",
                               "Direct Net of Home","Direct Home","Direct All","Paid Brand","GMV"))


```

## Organic Net Of Home Channel

```{r echo=FALSE, message=FALSE}
var_name="organic.net.home"
study_var=channel_sessions_long[,which(names(channel_sessions_long)==var_name)][[1]]

na_inds=which(is.na(study_var))
tv=channel_sessions_long$tv.spend[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]
title_paste="TV Spending (Dollars)"

```

###Trend Decomposition
The graph below decomposes the time series into 3 parts. The first sub-graph is a simple plot of observed behavior over time. The second sub-graph is the seasonal factor. This data spans two years. We considered each year to be one season, as such the seasonal plot repeats itself once. The third sub-graph shows the larger smoothed trend of the entire span of data. The fourth sub-graph shows the residual values of the trend line and seasonal element, that is, how far from the true values the trend line and seasonal element is at each point in time. We can see that the residuals are not unrelated to time. This is diagnostic of trend behavior that can be accounted for using a time-series model.
```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
stl_func(study_var,freq)

```



###ARIMAX model with TV spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
tv_arima=arima_func(stepwise_model,study_var,tv,freq)
# arima_func_sub(tv_arima,stepwise_model,study_var,tv,freq)

  arima.order=as.character(arimaorder(tv_arima))
  if (length(arima.order)>3){
    p_s=as.numeric(arima.order[5])
    d_s=as.numeric(arima.order[6])
  } else {
    p_s=0
    d_s=0
  }
  p=as.numeric(arima.order[1])
  d=as.numeric(arima.order[2])
  
  
  combined_obs=p+d+p_s+d_s+1
  

```


The graph below shows the general effect on TV spending on site visits by this channel. In this case the model is a combination of `r combined_obs -1`  lagged varialble(s). This representation of the model can be thought of as the expected gain in site visits dissipated over `r combined_obs` weeks per dollar spent on TV advertising dissipated over `r combined_obs` weeks.




```{r echo=FALSE, message=FALSE}

# model_comp_plots(stepwise_model,tv_arima)
transformed_plot(tv_arima,tv,title_paste)
  
 

```

The graph below shows the estimates of TV spending lift over time.

```{r echo=FALSE, message=FALSE, warning=FALSE}

# model_comp_plots(stepwise_model,tv_arima)
transformed_plot_by_date(channel_sessions_long,tv_arima,var_name)

```


###Forecasts
The graph below shows the model fit and prediction intervals. It is important to note that predicition intervals, unlike confidence intervals, expand over time. This means that any forecast model should only be relied upon for short forecast periods. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
channel_sessions_long=add_forecast_to_df(channel_sessions_long,tv_arima,var_name)

# channel_sessions_long=channel_sessions_long %>% rename(organic.net.home.forecast=forecast) 
   # plot(channel_sessions_long$organic.net.home.forecast)
   # lines(study_var)

```  


## Organic Home Channel

```{r echo=FALSE, message=FALSE}
var_name="organic.home"
study_var=channel_sessions_long[,which(names(channel_sessions_long)==var_name)][[1]]


na_inds=which(is.na(study_var))
tv=channel_sessions_long$tv.spend[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="TV Spending (Dollars)"
```

###Trend Decomposition
The graph below decomposes the time series into 3 parts. The first sub-graph is a simple plot of observed behavior over time. The second sub-graph is the seasonal factor. This data spans two years. We considered each year to be one season, as such the seasonal plot repeats itself once. The third sub-graph shows the larger smoothed trend of the entire span of data. The fourth sub-graph shows the residual values of the trend line and seasonal element, that is, how far from the true values the trend line and seasonal element is at each point in time. We can see that the residuals are not unrelated to time. This is diagnostic of trend behavior that can be accounted for using a time-series model.

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
stl_func(study_var,freq)

```


###ARIMAX model with TV spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
tv_arima=arima_func(stepwise_model,study_var,tv,freq)
# arima_func_sub(tv_arima,stepwise_model,study_var,tv,freq)

  arima.order=as.character(arimaorder(tv_arima))
  if (length(arima.order)>3){
    p_s=as.numeric(arima.order[5])
    d_s=as.numeric(arima.order[6])
  } else {
    p_s=0
    d_s=0
  }
  p=as.numeric(arima.order[1])
  d=as.numeric(arima.order[2])
  
  
  combined_obs=p+d+p_s+d_s+1
  

```


The graph below shows the general effect on TV spending on site visits by this channel. In this case the model is a combination of `r combined_obs -1`  lagged varialble(s). This representation of the model can be thought of as the expected gain in site visits dissipated over `r combined_obs` weeks per dollar spent on TV advertising dissipated over `r combined_obs` weeks.


```{r echo=FALSE, message=FALSE}

# model_comp_plots(stepwise_model,tv_arima)
transformed_plot(tv_arima,tv,title_paste)
   

```

The graph below shows the estimates of TV spending lift over time.

```{r echo=FALSE, message=FALSE, warning=FALSE}

# model_comp_plots(stepwise_model,tv_arima)
transformed_plot_by_date(channel_sessions_long,tv_arima,var_name)

```


###Forecasts
The graph below shows the model fit and prediction intervals. It is important to note that predicition intervals, unlike confidence intervals, expand over time. This means that any forecast model should only be relied upon for short forecast periods. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
channel_sessions_long=add_forecast_to_df(channel_sessions_long,tv_arima,var_name)


# channel_sessions_long=channel_sessions_long %>% rename(organic.home.forecast=forecast) 
   # plot(channel_sessions_long$organic.net.home.forecast)
   # lines(study_var)

```  


## Organic All Channel

```{r echo=FALSE, message=FALSE}
var_name="organic.all"
study_var=channel_sessions_long[,which(names(channel_sessions_long)==var_name)][[1]]


na_inds=which(is.na(study_var))
tv=channel_sessions_long$tv.spend[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="TV Spending (Dollars)"
```

###Trend Decomposition
The graph below decomposes the time series into 3 parts. The first sub-graph is a simple plot of observed behavior over time. The second sub-graph is the seasonal factor. This data spans two years. We considered each year to be one season, as such the seasonal plot repeats itself once. The third sub-graph shows the larger smoothed trend of the entire span of data. The fourth sub-graph shows the residual values of the trend line and seasonal element, that is, how far from the true values the trend line and seasonal element is at each point in time. We can see that the residuals are not unrelated to time. This is diagnostic of trend behavior that can be accounted for using a time-series model.

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
stl_func(study_var,freq)

```


###ARIMAX model with TV spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
tv_arima=arima_func(stepwise_model,study_var,tv,freq)
# arima_func_sub(tv_arima,stepwise_model,study_var,tv,freq)

  arima.order=as.character(arimaorder(tv_arima))
  if (length(arima.order)>3){
    p_s=as.numeric(arima.order[5])
    d_s=as.numeric(arima.order[6])
  } else {
    p_s=0
    d_s=0
  }
  p=as.numeric(arima.order[1])
  d=as.numeric(arima.order[2])
  
  
  combined_obs=p+d+p_s+d_s+1
  

```


The graph below shows the general effect on TV spending on site visits by this channel. In this case the model is a combination of `r combined_obs -1`  lagged varialble(s). This representation of the model can be thought of as the expected gain in site visits dissipated over `r combined_obs` weeks per dollar spent on TV advertising dissipated over `r combined_obs` weeks.


```{r echo=FALSE, message=FALSE}

# model_comp_plots(stepwise_model,tv_arima)
transformed_plot(tv_arima,tv,title_paste)
   

```

The graph below shows the estimates of TV spending lift over time.

```{r echo=FALSE, message=FALSE, warning=FALSE}

# model_comp_plots(stepwise_model,tv_arima)
transformed_plot_by_date(channel_sessions_long,tv_arima,var_name)

```


###Forecasts
The graph below shows the model fit and prediction intervals. It is important to note that predicition intervals, unlike confidence intervals, expand over time. This means that any forecast model should only be relied upon for short forecast periods. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
channel_sessions_long=add_forecast_to_df(channel_sessions_long,tv_arima,var_name)


# channel_sessions_long=channel_sessions_long %>% rename(organic.home.forecast=forecast) 
   # plot(channel_sessions_long$organic.net.home.forecast)
   # lines(study_var)

```  


## Direct Net of Home Channel

```{r echo=FALSE, message=FALSE}
var_name="direct.net.home"
study_var=channel_sessions_long[,which(names(channel_sessions_long)==var_name)][[1]]


na_inds=which(is.na(study_var))
tv=channel_sessions_long$tv.spend[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="TV Spending (Dollars)"
```



###Trend Decomposition
The graph below decomposes the time series into 3 parts. The first sub-graph is a simple plot of observed behavior over time. The second sub-graph is the seasonal factor. This data spans two years. We considered each year to be one season, as such the seasonal plot repeats itself once. The third sub-graph shows the larger smoothed trend of the entire span of data. The fourth sub-graph shows the residual values of the trend line and seasonal element, that is, how far from the true values the trend line and seasonal element is at each point in time. We can see that the residuals are not unrelated to time. This is diagnostic of trend behavior that can be accounted for using a time-series model.
```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
stl_func(study_var,freq)

```

###ARIMAX model with TV spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
tv_arima=arima_func(stepwise_model,study_var,tv,freq)
# arima_func_sub(tv_arima,stepwise_model,study_var,tv,freq)

  arima.order=as.character(arimaorder(tv_arima))
  if (length(arima.order)>3){
    p_s=as.numeric(arima.order[5])
    d_s=as.numeric(arima.order[6])
  } else {
    p_s=0
    d_s=0
  }
  p=as.numeric(arima.order[1])
  d=as.numeric(arima.order[2])
  
  
  combined_obs=p+d+p_s+d_s+1
  

```


The graph below shows the general effect on TV spending on site visits by this channel. In this case the model is a combination of `r combined_obs -1`  lagged varialble(s). This representation of the model can be thought of as the expected gain in site visits dissipated over `r combined_obs` weeks per dollar spent on TV advertising dissipated over `r combined_obs` weeks.


```{r echo=FALSE, message=FALSE}

# model_comp_plots(stepwise_model,tv_arima)
transformed_plot(tv_arima,tv,title_paste)
 
```


The graph below shows the estimates of TV spending lift over time.

```{r echo=FALSE, message=FALSE, warning=FALSE}

# model_comp_plots(stepwise_model,tv_arima)
transformed_plot_by_date(channel_sessions_long,tv_arima,var_name)

```


###Forecasts

The graph below shows the model fit and prediction intervals. It is important to note that predicition intervals, unlike confidence intervals, expand over time. This means that any forecast model should only be relied upon for short forecast periods. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
channel_sessions_long=add_forecast_to_df(channel_sessions_long,tv_arima,var_name)


# channel_sessions_long=channel_sessions_long %>% rename(direct.net.home.forecast=forecast) 
   # plot(channel_sessions_long$organic.net.home.forecast)
   # lines(study_var)

```  


## Direct Home Channel

```{r echo=FALSE, message=FALSE}
var_name="direct.home"
study_var=channel_sessions_long[,which(names(channel_sessions_long)==var_name)][[1]]

na_inds=which(is.na(study_var))
tv=channel_sessions_long$tv.spend[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="TV Spending (Dollars)"
```

###Trend Decomposition
The graph below decomposes the time series into 3 parts. The first sub-graph is a simple plot of observed behavior over time. The second sub-graph is the seasonal factor. This data spans two years. We considered each year to be one season, as such the seasonal plot repeats itself once. The third sub-graph shows the larger smoothed trend of the entire span of data. The fourth sub-graph shows the residual values of the trend line and seasonal element, that is, how far from the true values the trend line and seasonal element is at each point in time. We can see that the residuals are not unrelated to time. This is diagnostic of trend behavior that can be accounted for using a time-series model.

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
stl_func(study_var,freq)

```


###ARIMAX model with TV spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
tv_arima=arima_func(stepwise_model,study_var,tv,freq)
# arima_func_sub(tv_arima,stepwise_model,study_var,tv,freq)

  arima.order=as.character(arimaorder(tv_arima))
  if (length(arima.order)>3){
    p_s=as.numeric(arima.order[5])
    d_s=as.numeric(arima.order[6])
  } else {
    p_s=0
    d_s=0
  }
  p=as.numeric(arima.order[1])
  d=as.numeric(arima.order[2])
  
  
  combined_obs=p+d+p_s+d_s+1
  

```


The graph below shows the general effect on TV spending on site visits by this channel. In this case the model is a combination of `r combined_obs -1`  lagged varialble(s). This representation of the model can be thought of as the expected gain in site visits dissipated over `r combined_obs` weeks per dollar spent on TV advertising dissipated over `r combined_obs` weeks.


```{r echo=FALSE, message=FALSE}

# model_comp_plots(stepwise_model,tv_arima)
transformed_plot(tv_arima,tv,title_paste)
  
   
  
```

The graph below shows the estimates of TV spending lift over time.

```{r echo=FALSE, message=FALSE, warning=FALSE}

# model_comp_plots(stepwise_model,tv_arima)
transformed_plot_by_date(channel_sessions_long,tv_arima,var_name)

```


###Forecasts
The graph below shows the model fit and prediction intervals. It is important to note that predicition intervals, unlike confidence intervals, expand over time. This means that any forecast model should only be relied upon for short forecast periods. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
channel_sessions_long=add_forecast_to_df(channel_sessions_long,tv_arima,var_name)


# channel_sessions_long=channel_sessions_long %>% rename(direct.home.forecast=forecast) 
   # plot(channel_sessions_long$organic.net.home.forecast)
   # lines(study_var)

```  



## Direct All Channel

```{r echo=FALSE, message=FALSE}
var_name="direct.all"
study_var=channel_sessions_long[,which(names(channel_sessions_long)==var_name)][[1]]

na_inds=which(is.na(study_var))
tv=channel_sessions_long$tv.spend[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="TV Spending (Dollars)"
```

###Trend Decomposition
The graph below decomposes the time series into 3 parts. The first sub-graph is a simple plot of observed behavior over time. The second sub-graph is the seasonal factor. This data spans two years. We considered each year to be one season, as such the seasonal plot repeats itself once. The third sub-graph shows the larger smoothed trend of the entire span of data. The fourth sub-graph shows the residual values of the trend line and seasonal element, that is, how far from the true values the trend line and seasonal element is at each point in time. We can see that the residuals are not unrelated to time. This is diagnostic of trend behavior that can be accounted for using a time-series model.

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
stl_func(study_var,freq)

```


###ARIMAX model with TV spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
tv_arima=arima_func(stepwise_model,study_var,tv,freq)
# arima_func_sub(tv_arima,stepwise_model,study_var,tv,freq)

  arima.order=as.character(arimaorder(tv_arima))
  if (length(arima.order)>3){
    p_s=as.numeric(arima.order[5])
    d_s=as.numeric(arima.order[6])
  } else {
    p_s=0
    d_s=0
  }
  p=as.numeric(arima.order[1])
  d=as.numeric(arima.order[2])
  
  
  combined_obs=p+d+p_s+d_s+1
  

```


The graph below shows the general effect on TV spending on site visits by this channel. In this case the model is a combination of `r combined_obs -1`  lagged varialble(s). This representation of the model can be thought of as the expected gain in site visits dissipated over `r combined_obs` weeks per dollar spent on TV advertising dissipated over `r combined_obs` weeks.


```{r echo=FALSE, message=FALSE}

# model_comp_plots(stepwise_model,tv_arima)
transformed_plot(tv_arima,tv,title_paste)
  
   
  
```

The graph below shows the estimates of TV spending lift over time.

```{r echo=FALSE, message=FALSE, warning=FALSE}

# model_comp_plots(stepwise_model,tv_arima)
transformed_plot_by_date(channel_sessions_long,tv_arima,var_name)

```


###Forecasts
The graph below shows the model fit and prediction intervals. It is important to note that predicition intervals, unlike confidence intervals, expand over time. This means that any forecast model should only be relied upon for short forecast periods. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
channel_sessions_long=add_forecast_to_df(channel_sessions_long,tv_arima,var_name)


# channel_sessions_long=channel_sessions_long %>% rename(direct.home.forecast=forecast) 
   # plot(channel_sessions_long$organic.net.home.forecast)
   # lines(study_var)

```  


## Paid Brand Channel

```{r echo=FALSE, message=FALSE}
var_name="paid.brand"
study_var=channel_sessions_long[,which(names(channel_sessions_long)==var_name)][[1]]
na_inds=which(is.na(study_var))
tv=channel_sessions_long$tv.spend[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="TV Spending (Dollars)"
```

###Trend Decomposition

The graph below decomposes the time series into 3 parts. The first sub-graph is a simple plot of observed behavior over time. The second sub-graph is the seasonal factor. This data spans two years. We considered 26 weeks to be one season, as such the seasonal plot repeats itself once. The third sub-graph shows the larger smoothed trend of the entire span of data. The fourth sub-graph shows the residual values of the trend line and seasonal element, that is, how far from the true values the trend line and seasonal element is at each point in time. We can see that the residuals are not unrelated to time. This is diagnostic of trend behavior that can be accounted for using a time-series model.

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
stl_func(study_var,freq)

```


###ARIMAX model with TV spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
tv_arima=arima_func(stepwise_model,study_var,tv,freq)
# arima_func_sub(tv_arima,stepwise_model,study_var,tv,freq)

  arima.order=as.character(arimaorder(tv_arima))
  if (length(arima.order)>3){
    p_s=as.numeric(arima.order[5])
    d_s=as.numeric(arima.order[6])
  } else {
    p_s=0
    d_s=0
  }
  p=as.numeric(arima.order[1])
  d=as.numeric(arima.order[2])
  
  
  combined_obs=p+d+p_s+d_s+1
  

```


The graph below shows the general effect on TV spending on site visits by this channel. In this case the model is a combination of `r combined_obs -1`  lagged varialble(s). This representation of the model can be thought of as the expected gain in site visits dissipated over `r combined_obs` weeks per dollar spent on TV advertising dissipated over `r combined_obs` weeks.


```{r echo=FALSE, message=FALSE}

# model_comp_plots(stepwise_model,tv_arima)
transformed_plot(tv_arima,tv,title_paste)
   
  

```

The graph below shows the estimates of TV spending lift over time.

```{r echo=FALSE, message=FALSE, warning=FALSE}

# model_comp_plots(stepwise_model,tv_arima)
transformed_plot_by_date(channel_sessions_long,tv_arima,var_name)

```

###Forecasts
The graph below shows the model fit and prediction intervals. It is important to note that predicition intervals, unlike confidence intervals, expand over time. This means that any forecast model should only be relied upon for short forecast periods. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
channel_sessions_long=add_forecast_to_df(channel_sessions_long,tv_arima,var_name)


# channel_sessions_long=channel_sessions_long %>% rename(paid.brand.forecast=forecast) 
   # plot(channel_sessions_long$organic.net.home.forecast)
   # lines(study_var)

```  

#Summary

After isolating TV spending from the independent trend and behavior of  we can see that the impact of highly significant. These models bring several utilities. First, the relative effect of tv spend on each channel can be discerned by comparing their model coefficients (to be delivered). Second, the transformed impact can inform an appropriate amount of funds to allocate in the future.  Third, the models can be used to forecast into the near future, which has potential fraud detection applications. All of these utilities will grow stronger as more data are gathered- allowing for adding seasonal comparison to the models. The models will also become more potent when provided with more granular data than a weekly aggregation.


#Appendix, Model Diagnostics



## Organic Net Home Channel

```{r echo=FALSE, message=FALSE}
var_name="organic.net.home"
study_var=channel_sessions_long[,which(names(channel_sessions_long)==var_name)][[1]]

na_inds=which(is.na(study_var))
tv=channel_sessions_long$tv.spend[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]
title_paste="Organic Net of Home"

```

###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be freq (weeks per year), but we don't have two full periods
poly_fit=report_poly_fit_2(study_var,tv)
report_poly_fit_2_sub(poly_fit,study_var)
```


###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
stepwise_model=step_model(study_var,tv)
```

```{r echo=FALSE, message=FALSE}
step_pander(stepwise_model)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

poly_plots(tv,study_var,poly_fit,stepwise_model)

```


###ARIMAX model with TV spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
tv_arima=arima_func(stepwise_model,study_var,tv,freq)
arima_func_sub(tv_arima,stepwise_model,study_var,tv,freq)
 
 
    
```


###Model Validation
```{r echo=FALSE, message=FALSE, warning=FALSE}
model_validation(tv_arima,study_var,tv,freq,date)

```


## Organic Home Channel

```{r echo=FALSE, message=FALSE}
var_name="organic.home"
study_var=channel_sessions_long[,which(names(channel_sessions_long)==var_name)][[1]]


na_inds=which(is.na(study_var))
tv=channel_sessions_long$tv.spend[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="Organic Home"
```

###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be freq (weeks per year), but we don't have two full periods
poly_fit=report_poly_fit_2(study_var,tv)
report_poly_fit_2_sub(poly_fit,study_var)
```


###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
stepwise_model=step_model(study_var,tv)
```

```{r echo=FALSE, message=FALSE}
step_pander(stepwise_model)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

poly_plots(tv,study_var,poly_fit,stepwise_model)

```



###ARIMAX model with TV spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
tv_arima=arima_func(stepwise_model,study_var,tv,freq)
arima_func_sub(tv_arima,stepwise_model,study_var,tv,freq)
 
 
```


###Model Validation
```{r echo=FALSE, message=FALSE, warning=FALSE}
model_validation(tv_arima,study_var,tv,freq,date)
```


## Organic All Channel

```{r echo=FALSE, message=FALSE}
var_name="organic.all"
study_var=channel_sessions_long[,which(names(channel_sessions_long)==var_name)][[1]]


na_inds=which(is.na(study_var))
tv=channel_sessions_long$tv.spend[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

```

###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be freq (weeks per year), but we don't have two full periods
poly_fit=report_poly_fit_2(study_var,tv)
report_poly_fit_2_sub(poly_fit,study_var)
```


###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
stepwise_model=step_model(study_var,tv)
```

```{r echo=FALSE, message=FALSE}
step_pander(stepwise_model)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

poly_plots(tv,study_var,poly_fit,stepwise_model)

```



###ARIMAX model with TV spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
tv_arima=arima_func(stepwise_model,study_var,tv,freq)
arima_func_sub(tv_arima,stepwise_model,study_var,tv,freq)
 
 
```


###Model Validation
```{r echo=FALSE, message=FALSE, warning=FALSE}
model_validation(tv_arima,study_var,tv,freq,date)
```




## Direct Net Home Channel

```{r echo=FALSE, message=FALSE}
var_name="direct.net.home"
study_var=channel_sessions_long[,which(names(channel_sessions_long)==var_name)][[1]]


na_inds=which(is.na(study_var))
tv=channel_sessions_long$tv.spend[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="Direct Net Home"
```


###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be freq (weeks per year), but we don't have two full periods
poly_fit=report_poly_fit_2(study_var,tv)
report_poly_fit_2_sub(poly_fit,study_var)
```


###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
stepwise_model=step_model(study_var,tv)
```

```{r echo=FALSE, message=FALSE}
step_pander(stepwise_model)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

poly_plots(tv,study_var,poly_fit,stepwise_model)

```


###ARIMAX model with TV spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
tv_arima=arima_func(stepwise_model,study_var,tv,freq)
arima_func_sub(tv_arima,stepwise_model,study_var,tv,freq)
 
 
```


###Model Validation
```{r echo=FALSE, message=FALSE, warning=FALSE}
model_validation(tv_arima,study_var,tv,freq,date)
```


## Direct Home Channel

```{r echo=FALSE, message=FALSE}
var_name="direct.home"
study_var=channel_sessions_long[,which(names(channel_sessions_long)==var_name)][[1]]

na_inds=which(is.na(study_var))
tv=channel_sessions_long$tv.spend[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="Direct Home"
```

###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be freq (weeks per year), but we don't have two full periods
poly_fit=report_poly_fit_2(study_var,tv)
report_poly_fit_2_sub(poly_fit,study_var)
```


###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
stepwise_model=step_model(study_var,tv)
```

```{r echo=FALSE, message=FALSE}
step_pander(stepwise_model)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

poly_plots(tv,study_var,poly_fit,stepwise_model)

```


###ARIMAX model with TV spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
tv_arima=arima_func(stepwise_model,study_var,tv,freq)
arima_func_sub(tv_arima,stepwise_model,study_var,tv,freq)
 
 
```


###Model Validation
```{r echo=FALSE, message=FALSE, warning=FALSE}
model_validation(tv_arima,study_var,tv,freq,date)
```




## Direct All Channel

```{r echo=FALSE, message=FALSE}
var_name="direct.all"
study_var=channel_sessions_long[,which(names(channel_sessions_long)==var_name)][[1]]

na_inds=which(is.na(study_var))
tv=channel_sessions_long$tv.spend[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

```

###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be freq (weeks per year), but we don't have two full periods
poly_fit=report_poly_fit_2(study_var,tv)
report_poly_fit_2_sub(poly_fit,study_var)
```


###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
stepwise_model=step_model(study_var,tv)
```

```{r echo=FALSE, message=FALSE}
step_pander(stepwise_model)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

poly_plots(tv,study_var,poly_fit,stepwise_model)

```


###ARIMAX model with TV spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
tv_arima=arima_func(stepwise_model,study_var,tv,freq)
arima_func_sub(tv_arima,stepwise_model,study_var,tv,freq)
 
 
```


###Model Validation
```{r echo=FALSE, message=FALSE, warning=FALSE}
model_validation(tv_arima,study_var,tv,freq,date)
```


## Paid Brand Channel

```{r echo=FALSE, message=FALSE}
var_name="paid.brand"
study_var=channel_sessions_long[,which(names(channel_sessions_long)==var_name)][[1]]
na_inds=which(is.na(study_var))
tv=channel_sessions_long$tv.spend[-na_inds]
study_var=na.omit(study_var)
date=channel_sessions_long$date[-na_inds]

title_paste="Paid Brand"
```

###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
#frequency shoud be freq (weeks per year), but we don't have two full periods
poly_fit=report_poly_fit_2(study_var,tv)
report_poly_fit_2_sub(poly_fit,study_var)
```


###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
stepwise_model=step_model(study_var,tv)
```

```{r echo=FALSE, message=FALSE}
step_pander(stepwise_model)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

poly_plots(tv,study_var,poly_fit,stepwise_model)

```


###ARIMAX model with TV spend
```{r echo=FALSE, message=FALSE, warning=FALSE}
tv_arima=arima_func(stepwise_model,study_var,tv,freq)
arima_func_sub(tv_arima,stepwise_model,study_var,tv,freq)
 
 
```



###Model Validation
```{r echo=FALSE, message=FALSE, warning=FALSE}
model_validation(tv_arima,study_var,tv,freq,date)
```

