---
title: "TV Channel Models"
output: pdf_document
---

```{r echo=FALSE, message=FALSE} 
library(tidyr)
library(dplyr)
library(openxlsx)
library(lubridate)
library(ggplot2)
library(gridExtra)
library(forecast)
library(stats)
library(pander)
```



````{r echo=FALSE, message=FALSE}
tv_data=tbl_df(read.xlsx("tvanalysis.xlsx",sheet=2,rows=c(1:95),cols=c(1,4:20)))
tv_data$date=as.Date(as.character(tv_data$date),"%m/%d/%Y")+years(2000)
na_inds=which(is.na(tv_data$date))
for (ind in na_inds) {tv_data$date[ind]=tv_data$date[(ind-1)]+weeks(1)}

#Subsetting data
study_vars=c("date","tv.spend","organic","organic.home","direct.home","paid.brand.sessions")
study_cols=which(names(tv_data) %in% study_vars)
sub_study=na.omit(tv_data[,study_cols]  %>% arrange(desc(date)))
sub_study=sub_study[-1,]
sub_study$paid.brand.sessions=as.numeric(as.character(sub_study$paid.brand.sessions))
```


## Organic Channel
###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
poly_fit=lm(data=sub_study,organic~tv.spend+I(tv.spend^2))

tmp_df=data.frame(round(coef(poly_fit),3))
tmp_df=rbind(tmp_df,cor(fitted(poly_fit),sub_study$organic)^2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
print(tmp_df)
```


###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
big_poly_fit=lm(data=sub_study,organic~tv.spend+I(tv.spend^2)+I(tv.spend^3)+I(tv.spend^4))
stepwise_model=step(big_poly_fit,k=log(nrow(mtcars)))
```

```{r echo=FALSE, message=FALSE}
tmp_df=data.frame(round(coef(stepwise_model),3))
tmp_df=rbind(tmp_df,cor(fitted(stepwise_model),sub_study$organic)^2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
print(tmp_df)
```

Model diagnostics show strong autocorrelation in the data and evidence of seasonality. This suggests we build a model using the same tv spending coefficients isolating temporal factors.

```{r echo=FALSE, message=FALSE,warning=FALSE}
acf(stepwise_model$residuals,ylab="Correlation",main="Autocorrelation of Residuals")
```


```{r echo=FALSE, message=FALSE}
stl_obj=stl(ts(sub_study$organic, frequency = 26), s.window="periodic",robust=TRUE)
plot(stl_obj)+title("Organic Seasonal Decomposition")
```

###Arima model with TV spend
```{r echo=FALSE, message=FALSE}
xreg_matrix<-model.matrix(formula(stepwise_model),data=sub_study)
xreg_matrix=xreg_matrix[,-1]
tv_arima=auto.arima(sub_study$organic,xreg=xreg_matrix,max.p=10)

tv_arima_fcast=forecast(tv_arima,xreg=xreg_matrix)
plot(tv_arima_fcast)
tv_arima_R2=round(cor(fitted(tv_arima_fcast),sub_study$organic)^2,2)


tmp_df=data.frame(coef(tv_arima))
tmp_df=rbind(tmp_df,tv_arima_R2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
print(tmp_df)
```








## Organic Home Channel

###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
poly_fit=lm(data=sub_study,organic.home~tv.spend+I(tv.spend^2))

tmp_df=data.frame(round(coef(poly_fit),3))
tmp_df=rbind(tmp_df,cor(fitted(poly_fit),sub_study$organic.home)^2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
print(tmp_df)
```



###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
big_poly_fit=lm(data=sub_study,organic.home~tv.spend+I(tv.spend^2)+I(tv.spend^3)+I(tv.spend^4))
stepwise_model=step(big_poly_fit,k=log(nrow(mtcars)))
```

```{r echo=FALSE, message=FALSE}
tmp_df=data.frame(round(coef(stepwise_model),3))
tmp_df=rbind(tmp_df,cor(fitted(stepwise_model),sub_study$organic.home)^2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
print(tmp_df)
```


Model diagnostics show strong autocorrelation in the data and evidence of seasonality. This suggests we build a model using the same tv spending coefficients isolating temporal factors.

```{r echo=FALSE, message=FALSE,warning=FALSE}
acf(stepwise_model$residuals,ylab="Correlation",main="Autocorrelation of Residuals")
```

```{r echo=FALSE, message=FALSE}
stl_obj=stl(ts(sub_study$organic.home, frequency = 26), s.window="periodic",robust=TRUE)
plot(stl_obj)+title("Organic Home Seasonal Decomposition")
```

###Arima model with TV spend
```{r echo=FALSE, message=FALSE}
xreg_matrix<-model.matrix(formula(stepwise_model),data=sub_study)
xreg_matrix=xreg_matrix[,-1]

tv_arima=auto.arima(sub_study$organic.home,xreg=xreg_matrix,max.p=10)

tv_arima_fcast=forecast(tv_arima,xreg=xreg_matrix)
plot(tv_arima_fcast)
tv_arima_R2=round(cor(fitted(tv_arima_fcast),sub_study$organic.home)^2,2)


tmp_df=data.frame(coef(tv_arima))
tmp_df=rbind(tmp_df,tv_arima_R2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
print(tmp_df)
```




## Direct Home Channel
###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
poly_fit=lm(data=sub_study,direct.home~tv.spend+I(tv.spend^2))

tmp_df=data.frame(round(coef(poly_fit),3))
tmp_df=rbind(tmp_df,cor(fitted(poly_fit),sub_study$direct.home)^2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
print(tmp_df)
```


###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
big_poly_fit=lm(data=sub_study,direct.home~tv.spend+I(tv.spend^2)+I(tv.spend^3)+I(tv.spend^4))
stepwise_model=step(big_poly_fit,k=log(nrow(mtcars)))
```

```{r echo=FALSE, message=FALSE}
tmp_df=data.frame(round(coef(stepwise_model),3))
tmp_df=rbind(tmp_df,cor(fitted(stepwise_model),sub_study$direct.home)^2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
print(tmp_df)
```

Model diagnostics show strong autocorrelation in the data and evidence of seasonality. This suggests we build a model using the same tv spending coefficients isolating temporal factors.

```{r echo=FALSE, message=FALSE,warning=FALSE}
acf(stepwise_model$residuals,ylab="Correlation",main="Autocorrelation of Residuals")
```


```{r echo=FALSE, message=FALSE}
stl_obj=stl(ts(sub_study$direct.home, frequency = 26), s.window="periodic",robust=TRUE)
plot(stl_obj)+title("Direct Home Seasonal Decomposition")
```

###Arima model with TV spend
```{r echo=FALSE, message=FALSE}
xreg_matrix<-model.matrix(formula(stepwise_model),data=sub_study)
xreg_matrix=xreg_matrix[,-1]
tv_arima=auto.arima(sub_study$direct.home,xreg=xreg_matrix,max.p=10)

tv_arima_fcast=forecast(tv_arima,xreg=xreg_matrix)
plot(tv_arima_fcast)
tv_arima_R2=round(cor(fitted(tv_arima_fcast),sub_study$direct.home)^2,2)


tmp_df=data.frame(coef(tv_arima))
tmp_df=rbind(tmp_df,tv_arima_R2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
print(tmp_df)
```




## Paid Brand Channel

###2nd order polynomial fit
```{r echo=FALSE, message=FALSE}
poly_fit=lm(data=sub_study,paid.brand.sessions~tv.spend+I(tv.spend^2))

tmp_df=data.frame(round(coef(poly_fit),3))
tmp_df=rbind(tmp_df,cor(fitted(poly_fit),sub_study$paid.brand.sessions)^2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
print(tmp_df)
```


###Stepwise polynomial fit
```{r echo=FALSE, message=FALSE, results="hide"}
big_poly_fit=lm(data=sub_study,paid.brand.sessions~tv.spend+I(tv.spend^2)+I(tv.spend^3)+I(tv.spend^4))
stepwise_model=step(big_poly_fit,k=log(nrow(mtcars)))
```

```{r echo=FALSE, message=FALSE}
tmp_df=data.frame(round(coef(stepwise_model),3))
tmp_df=rbind(tmp_df,cor(fitted(stepwise_model),sub_study$paid.brand.sessions)^2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
print(tmp_df)
```


Model diagnostics show strong autocorrelation in the data and evidence of seasonality. This suggests we build a model using the same tv spending coefficients isolating temporal factors.

```{r echo=FALSE, message=FALSE,warning=FALSE}
acf(stepwise_model$residuals,ylab="Correlation",main="Autocorrelation of Residuals")
```


```{r echo=FALSE, message=FALSE}
stl_obj=stl(ts(sub_study$paid.brand.sessions, frequency = 26), s.window="periodic",robust=TRUE)
plot(stl_obj)+title("Paid Brand Decomposition")
```

###Arima model with TV spend
```{r echo=FALSE, message=FALSE}
xreg_matrix<-model.matrix(formula(stepwise_model),data=sub_study)
xreg_matrix=xreg_matrix[,-1]
tv_arima=auto.arima(sub_study$paid.brand.sessions,xreg=xreg_matrix,max.p=10)

tv_arima_fcast=forecast(tv_arima,xreg=xreg_matrix)
plot(tv_arima_fcast)
tv_arima_R2=round(cor(fitted(tv_arima_fcast),sub_study$paid.brand.sessions)^2,2)


tmp_df=data.frame(coef(tv_arima))
tmp_df=rbind(tmp_df,tv_arima_R2)
rownames(tmp_df)[length(rownames(tmp_df))]="R2"
print(tmp_df)
```



