---
title: "Vendor Channel Attribution"
author: "Jeffrey Uslan"
date: "November 17, 2015"
output: html_document
---

#Synopsis
This report explores the contribution of site visit touch points on order completion. The purpose of this exploration is to assign appropriate "credit" for a purchase to the appropriate vendors. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
#Initial data munging

library(tidyr)
library(dplyr)
library(corrplot)
library(glmnet)
library(readr)
library(caret)
library(randomForest)
library(pander)
panderOptions('table.style',"simple")
panderOptions('table.split.cells',"Inf")
panderOptions('table.split.table',"Inf")


source("Ritani_log_analysis_DB_connection.R")
###



#####imorting purchasers
query=paste("
            SELECT order_number, name AS channel, state,
            max(total) AS revenue, count(*) as session_count
            FROM (
            SELECT channel_id, clickstream_id, session_id
            FROM channel_touchpoints
            ) ct INNER JOIN (
            SELECT id, name, has_attributed_revenue
            FROM channels
            ) ch ON ct.channel_id=ch.id
            INNER JOIN (
            SELECT id, pre_purchase
            FROM sessions
            WHERE pre_purchase=1
            ) se ON ct.session_id=se.id
            INNER JOIN (
            SELECT id, order_number, total, state
            FROM clickstreams
            ) cl ON ct.clickstream_id=cl.id
            GROUP BY order_number, channel
            HAVING state LIKE '%shipped%' OR state LIKE '%accepted%' OR state LIKE '%delivered%'
            OR state LIKE '%store%' OR state LIKE '%charged%' OR state LIKE '%authorized%'
            OR state LIKE '%shipped%'
            ")

data_long=tbl_df(dbGetQuery(con,query))

#ditching some data
data_long$state=NULL
data_long$revenue=NULL
data_long$revenue=NULL
data_long$purchaser=1

# Importing non-purschasers
non_purchaser_data=tbl_df(read_csv(file=gzfile('non-purchaser-channels.csv.gz'),col_names=FALSE))
non_purchaser_data=non_purchaser_data %>% rename(Time=X1) 
# non_purchaser_data$Time=NULL
non_purchaser_data$X4=NULL
non_purchaser_data$purchaser=0
non_purchaser_data$session_count=1
non_purchaser_data=non_purchaser_data %>% rename(order_number=X2) 
non_purchaser_data=non_purchaser_data %>% rename(channel=X3)



#omit visit within 30 minutes of each other
non_purchaser_data=non_purchaser_data %>% arrange(order_number,channel,Time)

non_purchaser_data=non_purchaser_data %>% group_by(order_number,channel) %>%
  mutate(duration = c(1,diff(Time))*(60*24))
short_visit_inds=which(non_purchaser_data$duration<30 & non_purchaser_data$duration>=0)
# non_purchaser_data %>% group_by(channel,purchaser) %>%  summarise(sessions=n()) %>% arrange(channel,purchaser)
# non_purchaser_data[-short_visit_inds,] %>% group_by(channel,purchaser) %>%  summarise(sessions=n()) %>% arrange(channel,purchaser)

non_purchaser_data=non_purchaser_data[-short_visit_inds,]


non_purchaser_data$duration=NULL
non_purchaser_data$Time=NULL

#combine data
data_long=rbind(data_long,non_purchaser_data)



# data_long$purchaser=as.factor(data_long$purchaser)

#cleaning some unneccesary 
data_long=data_long[-which(data_long$channel=="unknown"),]
data_long=data_long[-which(data_long$channel=="social"),]
data_long=data_long[-grep("retailer",data_long$channel),]
data_long=data_long[-which(data_long$channel=="tv"),]
data_long=data_long[-which(data_long$channel=="session continuation"),]

#reassign some channel names
disp_inds=grep("display",data_long$channel)
data_long$channel[disp_inds]="display"

email_inds=grep("email",data_long$channel)
data_long$channel[email_inds]="email"

email_inds=grep("paid",data_long$channel)
data_long$channel[email_inds]="paid"

email_inds=grep("organic",data_long$channel)
data_long$channel[email_inds]="organic"

#combine displays and combine emails by order
data_long=data_long %>% group_by(order_number,channel) %>% 
  summarise(session_count=sum(session_count),purchaser=first(purchaser))

```


#Exploration

The table below shows how many users are present in the purchase group and non-purchaser group.
```{r echo=FALSE}
pander(data_long %>% group_by(purchaser) %>%  summarise(Users=n()) %>% arrange(desc(Users)))
```

The table below shows how users are distributed across each visit touch point and purchaser group. Note that that this tabulation does not account for users visiting multiple touch points, a common occurence.
```{r echo=FALSE}
#recheck channel distribution with corrections
pander(data_long %>% group_by(channel,purchaser) %>%  summarise(Users=n()) %>% arrange(channel,purchaser))
```



```{r echo=FALSE}

# putting data in wide form
 # data_wide=resampled_data_frame %>%  spread(key=channel,value=session_count)
data_wide=data_long %>%  spread(key=channel,value=session_count)

#setting all missings to 0
numeric_inds=sapply(data_wide,is.numeric)
data_wide[,numeric_inds]=apply(data_wide[,numeric_inds],2,function(x){
  na_inds=which(is.na(x))
  if (length(na_inds)>0){
    x[na_inds]=0  
  } else {
    x
  }
  x
})

#combining orders for total sessions by each channel
data_wide=data_wide %>% group_by(order_number) %>%  summarise(purchaser=first(purchaser),affiliates=sum(affiliates),                                                             direct=sum(direct),display=sum(display),email=sum(email),                                                             organic=sum(organic),paid=sum(paid),referral=sum(referral))
#order_number is irrelevant now
data_wide$order_number=NULL


##Sanity checks
row_sums=apply(data_wide[,2:8],1,function(x){sum(x)})
# summary(row_sums)
# sd(row_sums)

high_inds=which(row_sums> (mean(row_sums)+10*sd(row_sums)))
if (length(high_inds)) data_wide=data_wide[-high_inds,]
```

The table below shows the mean number of sessions at each visit touch point across purchaser groups. T-tests were performed for each variable and all tests, except the display, show that the differences between purchaser groups are statistically significant. The display touch point had a p-value of 0.21- implying that the mean display sessions were not different between purchasers and non-purchasers.

```{r echo=FALSE}
row_sums=apply(data_wide[,2:8],1,function(x){sum(x)})
data_wide$row_sums=row_sums
pander(((data_wide %>% group_by(purchaser) %>% summarise(row_sums=mean(row_sums),
                                                affiliates=mean(affiliates),
                                                direct=mean(direct),
                                                display=mean(display),
                                                email=mean(email),
                                                organic=mean(organic),
                                                paid=mean(paid),
                                                referral=mean(referral))))
,digits=2)


data_wide$row_sums=NULL
```


```{r echo=FALSE, eval=FALSE}
#t test total sessions- ss diff
t.test(as.vector(data_wide %>% filter(purchaser==0) %>% select(row_sums))[[1]],
       as.vector(data_wide %>% filter(purchaser==1) %>% select(row_sums))[[1]])

#t test affiliates- ss diff
t.test(as.vector(data_wide %>% filter(purchaser==0) %>% select(affiliates))[[1]],
       as.vector(data_wide %>% filter(purchaser==1) %>% select(affiliates))[[1]])
#t test direct- ss diff
t.test(as.vector(data_wide %>% filter(purchaser==0) %>% select(direct))[[1]],
       as.vector(data_wide %>% filter(purchaser==1) %>% select(direct))[[1]])
#t test display- no diff
t.test(as.vector(data_wide %>% filter(purchaser==0) %>% select(display))[[1]],
       as.vector(data_wide %>% filter(purchaser==1) %>% select(display))[[1]])
#t test email- ss diff
t.test(as.vector(data_wide %>% filter(purchaser==0) %>% select(email))[[1]],
       as.vector(data_wide %>% filter(purchaser==1) %>% select(email))[[1]])
#t test organic- ss diff
t.test(as.vector(data_wide %>% filter(purchaser==0) %>% select(organic))[[1]],
       as.vector(data_wide %>% filter(purchaser==1) %>% select(organic))[[1]])
#t test paid- ss diff
t.test(as.vector(data_wide %>% filter(purchaser==0) %>% select(paid))[[1]],
       as.vector(data_wide %>% filter(purchaser==1) %>% select(paid))[[1]])
#t test referral- ss diff
t.test(as.vector(data_wide %>% filter(purchaser==0) %>% select(referral))[[1]],
       as.vector(data_wide %>% filter(purchaser==1) %>% select(referral))[[1]])
```

```{r echo=FALSE}
media_combo=apply(data_wide[,2:8],1,function(x){
  combo=as.character(as.numeric(as.numeric(x)>0))
  combo_word=""
  for (l in combo) combo_word=paste0(combo_word,l)
  combo_word
})

data_wide$media_combo=media_combo


```

The table below shows the 6 most prevalent combinations of touch points among non-purchasers and the average number of sessions within those touch points.
```{r echo=FALSE}
pander(data_wide %>% filter(purchaser==0) %>% group_by(media_combo) %>% mutate(Frequency=n()/length(which(data_wide$purchaser==0))) %>% summarise_each(funs(mean)) %>% arrange(desc(Frequency)) %>% head(),digits=2)

```



The table below shows the 6 most prevalent combinations of touch points among purchasers and the average number of sessions within those touch points.

```{r echo=FALSE}
pander(data_wide %>% filter(purchaser==1) %>% group_by(media_combo) %>% mutate(Frequency=n()/length(which(data_wide$purchaser==1))) %>% summarise_each(funs(mean)) %>% arrange(desc(Frequency)) %>% head(),digits=2)

data_wide$media_combo=NULL
```

The graph below shows the correlative relationships of each variable.
```{r echo=FALSE}
corrplot(cor(data_wide[,1:8]))
```

# Modeling

For validation purposes, the data were split into a training and test set. The split was made with 60% of the data alloted to model training and 40% to model testing.

```{r echo=FALSE}
#Checking out various models
set.seed(2)
inTrain = createDataPartition(y=data_wide$purchaser, p = .6)[[1]]
training = data_wide[ inTrain,]
testing = data_wide[-inTrain,]
```


The regularized regression classification model had an accuracy of 0.744 on the training data, 0.754 on the testing data, and 0.748 on all data.
```{r echo=FALSE}
fit1= lm(purchaser~.+0,data=training)


x <- model.matrix(formula(fit1),data=training)
y<- as.matrix(training$purchaser)
#DO NOT CHANGE ALPHA NOR LAMBDA
fit<-glmnet(x,y, family="gaussian", alpha=0.9, lambda=0.001,intercept=FALSE)
## summarize the fit
# coefficients(fit)
## make predictions
predictions <- predict(fit, x)
if (length(which(predictions>1))>0) predictions[which(predictions>1)]=1
## summarize accuracy
# confusionMatrix(y, round(predictions))


#checking accuracy on test set
x_test <- model.matrix(formula(fit1),data=testing)
y_test<- as.matrix(testing$purchaser)
predictions <- predict(fit, x_test)
if (length(which(predictions>1))>0) predictions[which(predictions>1)]=1
# confusionMatrix(y_test, round(predictions))

#checking accuracy over all
x_all <- model.matrix(formula(fit1),data=data_wide)
y_all<- as.matrix(data_wide$purchaser)
predictions <- predict(fit, x_all)
if (length(which(predictions>1))>0) predictions[which(predictions>1)]=1
# confusionMatrix(y_all, round(predictions))
```



The table below shows the coefficients produced by the linear classifier. These coefficients can be thought of as the additive probability of a purchase occuring per session.
```{r echo=FALSE}
coef_df=data.frame(Coefficients=coefficients(fit)[2:8])
rownames(coef_df)=(coefficients(fit))@Dimnames[[1]][2:8]
pander(coef_df,digits=2)
```


 The linear classifier coefficients do not immediately indicate the potency of each touch point as the distribution of sessions is different between touch points. To identify which touch points have the most predicitive power we fit a black box random forest classifier, a bootstrapped decision tree. We then extract the accuracy contributions. The figure below shows how much accuracy would be lost if a variable were to be removed.

```{r echo=FALSE, warning=FALSE}
data_wide$purchaser=as.factor(data_wide$purchaser)
 modFit <- randomForest(purchaser ~. , data=data_wide, importance = TRUE)
# rf_importances=importance(modFit, scale=FALSE)
 # getTree(modFit, k=1, labelVar=TRUE)
varImpPlot(modFit, type=1, scale=FALSE, main="Variable Importance")

```






